---
title: "Data cleaning of IAT_Audio_Swabian"
author: "Judit Vari"
date: "9 1 2024"
output: html_document
---

# load libraries
```{r setup, include=FALSE}
library (dplyr)
library(tidyr)
library(broom)
library(stringr)
library(readr)
library(stringdist)
library(lubridate)
library(here)

options(scipen=999)
```
# read data
```{r read, include=FALSE}
data_raw <- read_delim(here("raw_data", "jatos_results_data_17.01.24.csv"), col_names = TRUE, delim = ",")
```
# Multiple participation
identify participants who have multiple sessions

```{r multi part_1, include=FALSE}

data_raw %>%
  group_by (bilendi_id)%>%
  summarise (n_distinct (sessionid))-> multi_part 
```
# # Multiple participation

understand source for multi. participation

```{r multi part_2, include=FALSE}

data_raw %>%
  filter (bilendi_id == "264443801636864" | bilendi_id == "263320741943482" | bilendi_id == "263320741953628" | bilendi_id == "264559562072251" |  bilendi_id == "264560246627553" | bilendi_id == "265003370475767")%>%
  select (bilendi_id, sessionid, moment, meta_browser_codename, meta_system_os, meta_date_startdate, meta_date_starttime, stimulus_ID, trialcount, response_time, correct, feedback_q1, feedback_q2, age, gender)-> multi_pp

multi_pp%>%
  group_by(meta_system_os)%>%
  summarise(n_distinct(bilendi_id), n_distinct(sessionid))->sum_multi_pp # Mac: 4 Bilendi IDs 8x Session_ID, Windows: 2 bilendi_id & 5 x session_ID # kick Windows multiple session, keep Mac and take second session


multi_pp%>%
  filter(meta_system_os == "MacIntel")-> multi_pp_mac
   
multi_pp%>%
summarise(unique(multi_pp$bilendi_id), n_distinct(sessionid))-> multi_pp_mac_sum # 6 Bilendi IDs?
  
  # find later session

multi_pp_mac %>%
  mutate(timestamp = strptime(meta_date_starttime, format = "%H:%M:%S"),
         time_string = format(timestamp, format = "%H:%M:%S"),
         time_numeric = hour(timestamp) * 3600 + minute(timestamp) * 60 + second(timestamp)) -> multi_pp_mac


multi_pp_mac%>%
  group_by(bilendi_id)%>%
  slice_min(time_numeric)->pp_mac_singl

# quick and dirty # kick them all

data_raw %>%
  filter (bilendi_id != "264443801636864" & bilendi_id != "263320741943482" & bilendi_id != "263320741953628" & bilendi_id != "264559562072251" &  bilendi_id != "264560246627553" & bilendi_id != "265003370475767")-> data_raw

#check multi part

data_raw %>%
  group_by (bilendi_id)%>%
  summarise (n_distinct (sessionid))-> multi_part # worked

# how many rows per pp: between 194 & 198 rows

data_raw %>%
  group_by(bilendi_id, moment) %>%
  summarise(row_count = n()) -> check_rows_per_pp_moment

check_rows_per_pp_moment%>%
  ungroup()%>%
  filter (moment == "pre_selection") %>%
  summarise (max (row_count), min (row_count), mean (row_count))->sum_rows_per_preselect # max 7, min 3, mean 4


check_rows_per_pp_moment%>%
  ungroup()%>%
  filter (moment == "IAT") %>%
  summarise (max (row_count), min (row_count), mean (row_count))->sum_rows_per_IAT # almost all pp 190 rows but some 191 rows

check_rows_per_pp_moment%>%
  ungroup()%>%
  filter (moment == "questionnaire") %>%
  summarise (max (row_count), min (row_count), mean (row_count))->sum_rows_per_Q # all pp 1 row

# why different row no.s?
data_raw %>%
  group_by(bilendi_id) %>%
  filter(n()< 198) -> pp_low_row
```
# integrate Questionnaire data into IAT data
aim: each pre-selection as well as IAT observation row contains questionnaire data values
```{r cleaning_two_data_sets, include=FALSE}


# create two data sets
data_raw%>%
  filter(moment== "questionnaire")%>%
  select(bilendi_id, moment, age, bundesland, gender, education, education_other, employment_status, monthly_income, training, training2,             training_other, training_other2, family_member1, 
                     family_member1_other, family_member1_response, family_member2, 
                     family_member2_other, family_member2_response, family_member3,
          family_member3_other, family_member3_response, other_languages, 
                     ideology, ideology_no_answer, ideology_unknown, voting_behaviour, 
                     voting_other, populism1, populism2, populism3, populism4, 
                     statement1, statement2, statement3, statement4, statement5, 
                     statement6, statement7, statement8, statement9, feedback_q1, feedback_q2) -> Quest_data # 748


data_raw%>%
  filter(moment== "IAT" | moment== "pre_selection")%>%
  select(-age, -bundesland, -gender, -education, -education_other, -employment_status, -monthly_income, -training, -training2,          -training_other, -training_other2, -family_member1,                    -family_member1_other, -family_member1_response, -family_member2, -family_member2_other, -family_member2_response, -family_member3, -family_member3_other, -family_member3_response, -other_languages, 
                     -ideology, -ideology_no_answer, -ideology_unknown, -voting_behaviour, 
                     -voting_other, -populism1, -populism2, -populism3, -populism4, 
                    -statement1, -statement2, -statement3, -statement4, -statement5, 
                     -statement6, -statement7, -statement8, -statement9, -feedback_q1, -feedback_q2) -> data_IAT_Pre_selc # 145.819


# join tables

left_join(data_IAT_Pre_selc, Quest_data, by = c("bilendi_id"),  relationship = "many-to-many")-> data_raw
# 104 columns, 148.918 rows # moment.x & moment.y

missing_values_before <- data_raw %>%
  summarise(across(everything(), ~ sum(is.na(.))))
# no NAs created 

rename(data_raw, moment = moment.x)->data_raw

#how many rows per pp

data_raw %>%
  group_by(bilendi_id, moment) %>%
  summarise(row_count = n()) -> check_rows_per_pp_moment

data_raw%>%
filter(blockno != 8)->data_raw

```
# delete superfluous column names in values 
```{r clean_columns, include=FALSE}
# clean columns containing column names as values

columns_to_process <- c("populism1", "populism2", "populism3", "populism4", "statement1", "statement2", "statement3", "statement4", "statement5", "statement6", "statement7", "statement8", "statement9")

data_raw <- data_raw %>%
  mutate_at(vars(columns_to_process), funs(str_replace(., "\\w+-", "")))
```
# transform age variable
```{r age_clean, include=FALSE}

data_raw %>%
  filter (age >80)%>%
  summarise (n_distinct (bilendi_id)) -> pp_year

data_raw %>%
  filter (age >80)%>%
  distinct (bilendi_id, age) -> pp_year # two rubbish: 150 & 558, one 83 and one 1980

data_raw %>%
  filter (age< 18)%>%
  distinct (bilendi_id, age) -> pp_age_bad # 4 pp. two rubbish, two under aged?

data_raw%>%
  mutate(age = ifelse (age == 1980, 44, age))%>%
  mutate(age = ifelse (age < 18, 18, age))%>%
  mutate(age = ifelse (age > 83, NA, age)) -> data_raw

data_raw%>%
  distinct(bilendi_id, age)%>%
  summarise(sum(is.na(age)))-> age_NA # 4 NAs

data_raw%>%
  drop_na (age)%>%
  summarise(mean(age), sd (age), min (age), max (age))-> age_sum

```
# Rename variables
```{r rename variables, include=FALSE}
rename(data_raw, charisma_lang_var = right_dialect_trial) -> data_raw
rename(data_raw, start_iat = cat_order_iat) -> data_raw
rename(data_raw, pp_gender = gender) -> data_raw
```
# assign classes
```{r classes, include=FALSE}
data_raw$ideology <- as.numeric(data_raw$ideology)
data_raw$populism1 <- as.numeric(data_raw$populism1)
data_raw$populism2 <- as.numeric(data_raw$populism2)
data_raw$populism3 <- as.numeric(data_raw$populism3)
data_raw$populism4 <- as.numeric(data_raw$populism4)
data_raw$age <- as.numeric(data_raw$age)
data_raw$bilendi_id <- as.numeric(data_raw$bilendi_id)
data_raw$trialcount <- as.numeric(data_raw$trialcount)


data_raw$bundesland <- as.factor(data_raw$bundesland)
data_raw$education<- as.factor(data_raw$education)
data_raw$education_other<- as.factor(data_raw$education_other)
data_raw$employment_status<- as.factor(data_raw$employment_status)
data_raw$family_member1<- as.factor(data_raw$family_member1)
data_raw$family_member2<- as.factor(data_raw$family_member2)
data_raw$family_member3_<- as.factor(data_raw$family_member3)
data_raw$family_member1_other<- as.factor(data_raw$family_member1_other)
data_raw$family_member2_other<- as.factor(data_raw$family_member2_other)
data_raw$family_member3_other<- as.factor(data_raw$family_member3_other)
data_raw$pp_gender<- as.factor(data_raw$pp_gender)
data_raw$ideology_no_answer<- as.factor(data_raw$ideology_no_answer)
data_raw$ideology_unknown<- as.factor(data_raw$ideology_unknown)
data_raw$leadership_lang_var<- as.factor(data_raw$leadership_lang_var)
data_raw$left_dialect_trial<- as.factor(data_raw$left_dialect_trial)
data_raw$left_leadership_trial<- as.factor(data_raw$left_leadership_trial)
data_raw$moment<- as.factor(data_raw$moment)
data_raw$monthly_income<- as.factor(data_raw$monthly_income)
data_raw$speaker_gender<- as.factor(data_raw$speaker_gender)
data_raw$statement1 <- as.factor(data_raw$statement1)
data_raw$statement2 <- as.factor(data_raw$statement2)
data_raw$statement3 <- as.factor(data_raw$statement3)
data_raw$statement4 <- as.factor(data_raw$statement4)
data_raw$statement5 <- as.factor(data_raw$statement5)
data_raw$statement6 <- as.factor(data_raw$statement6)
data_raw$statement7 <- as.factor(data_raw$statement7)
data_raw$statement8 <- as.factor(data_raw$statement8)
data_raw$statement9 <- as.factor(data_raw$statement9)
data_raw$stim_cat<- as.factor(data_raw$stim_cat)
data_raw$training<- as.factor(data_raw$training)
data_raw$training2<- as.factor(data_raw$training2)
data_raw$training_other<- as.factor(data_raw$training_other)
data_raw$training_other2<- as.factor(data_raw$training_other2)
data_raw$voting_behaviour<- as.factor(data_raw$voting_behaviour)
data_raw$voting_other<- as.factor(data_raw$voting_other)
```
# Rename levels
```{r rename levels, include=FALSE}

data_raw%>%
  mutate (charisma_lang_var = ifelse(charisma_lang_var == "Dialekt", "vernacular", "standard"))->data_raw

#check 
unique(data_raw$charisma_lang_var)# standard"   "vernacular"
unique(data_raw$right_leadership_trial) # False &  mit Charisma
unique(data_raw$stim_cat) # "dialect2", dialect1", "leadership2", "leadership1"


#cat_order_iat
data_raw%>%
  mutate(start_iat = case_when(start_iat == 0 ~ "standard-with Charisma", start_iat == 1 ~ "vernacular-with Charisma", TRUE ~ "NA"))->data_raw

# check
unique(data_raw$start_iat)
```
# create new variables
```{r new variables, include=FALSE}
# create more general stimulus category variable 

data_raw%>% 
  mutate (stim_cat = ifelse (stim_cat == "dialect1" | stim_cat == "dialect2", "lang.var", "leadership"))-> result
unique(result$stim_cat)

# new variable: education & training

 result%>%
   mutate (sum_training = case_when
(training == "Berufsfachschulabschluss" ~ "low",
training == "Fachhochschulabschluss" ~ "high",
training == "Fachschulabschluss" ~ "middle",
training == "Hochschulabschluss (Bachelor)" ~ "high",
training == "Hochschulabschluss (Master)" ~ "high",
training == "Hochschulabschluss (Promotion)" ~ "high",
training == "Keinen" ~ "low",
training == "Meister/in, Technikerabschluss" ~ "middle",
training == "Teilfacharbeiterabschluss" ~ "low",
training == "abgeschlossene gewerbliche oder landwirtschaftliche Lehre" ~ "middle",
training == "abgeschlossene kaufmännische Lehre" ~ "middle",
training == "andere" ~ "middle",
training == "beruflich-betriebliche Anlernzeit mit Abschlusszeugnis, aber keine Lehre" ~ "low", TRUE ~ NA))-> result
 

 result%>%
   mutate (sum_education = case_when
(education == "Schule beendet ohne Abschluss"  ~ "low",
education == "Hauptschulabschluss, Volksschulabschluss, Abschluss der polytechnischen Oberschule 8. oder 9. Klasse" ~ "low",
education == "Realschulabschluss, Mittlere Reife, Fachschulreife oder Abschluss der polytechnischen Oberschule 10. Klasse" ~ "middle",
education == "Fachhochschulreife (Abschluss einer Fachoberschule etc.)" ~ "high",
education == "Abitur bzw. erweiterte Oberschule mit Abschluss 12. Klasse (Hochschulreife)" ~ "high",
education == "bin noch Schüler/in" ~ "still at school",
education == "andere" ~ "other",
education == "NA" ~ "NA", TRUE ~ NA))-> result
 
```
# clean pre-selection variables
```{r pre-select, include=FALSE}
# cat1_: leadership1 = „mit Charisma“
# cat2_: leadership2 = „ohne Charisma“
# cat1/2_list: Logging of final selection for leadership attributes of leadership category 1. Each attribute with associated rank
# cat1/2_top_6: Logging of top 6  selection of leadership attributes, used later for the IAT

# cat1_list,cat1_top_6, cat2_list, cat2_top_6 nested list variables 

result %>%
  filter(moment== "pre_selection")%>%
  select(bilendi_id, cat1_list, cat2_list)%>%
 mutate(cat1_list = str_remove_all(cat1_list, "\\[|\\]|'"))%>%
mutate(cat2_list = str_remove_all(cat2_list, "\\[|\\]|'"))%>% 
   separate(cat1_list, sep = ", ", into = c("chariAttribute_1", "char_rank_1", "chariAttribute_2", "char_rank_2", "chariAttribute_3", "char_rank_3", "chariAttribute_4", "char_rank_4", "chariAttribute_5", "char_rank_5", "chariAttribute_6", "char_rank_6", "chariAttribute_7", "char_rank_7", "chariAttribute_8", "char_rank_8", "chariAttribute_9", "char_rank_9", "chariAttribute_10", "char_rank_10"))%>% 
   separate(cat2_list, sep = ", ", into = c("wochariAttribute_1", "wo_char_rank_1", "wochariAttribute_2", "wo_char_rank_2", "wochariAttribute_3", "wo_char_rank_3", "wochariAttribute_4", "wo_char_rank_4", "wochariAttribute_5", "wo_char_rank_5", "wochariAttribute_6", "wo_char_rank_6", "wochariAttribute_7", "wo_char_rank_7", "wochariAttribute_8", "wo_char_rank_8", "wochariAttribute_9", "wo_char_rank_9", "wochariAttribute_10", "wo_char_rank_10"))%>%
  distinct()-> data_pre_select
 
 
data_pre_select%>%
  select(-char_rank_1, -char_rank_2, -char_rank_3, -char_rank_4, -char_rank_5, -char_rank_6, -char_rank_7, -char_rank_8, -char_rank_9, -char_rank_10, -wo_char_rank_1, -wo_char_rank_2, -wo_char_rank_3, -wo_char_rank_4, -wo_char_rank_5, -wo_char_rank_6, -wo_char_rank_7, -wo_char_rank_8, -wo_char_rank_9, -wo_char_rank_10, )-> data_pre_select

data_pre_select%>%
  pivot_longer(2:21, names_to = "Rank", values_to = "Pre_select_Attribute")%>%
  separate(Rank, sep = "_", into = c("Pre_select_type","Pre_select_Rank"))->data_pre_select

result%>%
  select(-cat1_top_6, -cat2_top_6, -cat1_list, -cat2_list)->result


write_delim(data_pre_select, here("data_processed", "result_preselect_clean.csv"), col_names = TRUE, delim = ",")
```
# Marlowe- Crowne social desirability score
```{r MCSD, include=FALSE}

# scoring: 1 for "true” to a socially desirable item or “false” to a socially undesirable item.
# scoring: 0 for “false” to a socially desirable item or “true” to a socially undesirable item.
# key: socially desirable answer: statement1-9 1 point for correct answer see key

# total score: summing up the scores for all items
# higher scores = higher SD/ “need for approval” 


# statement 1: Ich bin manchmal verärgert, wenn ich meinen Willen nicht bekomme. socially undesirable, key: FALSE
# statement 2: Ganz gleich mit wem ich mich unterhalte, ich bin immer ein/e gute/r ZuhörerIn. socially desirable key: TRUE
# statement 3: Es hat Situationen gegeben, in denen ich jemanden ausgenutzt habe. key: FALSE
# statement 4: Ich bin immer bereit zuzugeben, wenn ich einen Fehler mache; key: TRUE
# statement 5: Ich versuche manchmal, es jemandem heimzuzahlen, anstatt zu vergeben und zu vergessen.key: FALSE
# statement 6: Gelegentlich hatte ich Lust, Dinge zu zerschlagen. key: FALSE
# statement 7: Manchmal bin ich neidisch, wenn andere Glück haben; key: FALSE
# statement 8:Ich hatte niemals das Gefühl, ohne Grund bestraft zu werden; key: TRUE
# statement 9: Ich habe niemals mit Absicht etwas gesagt, was die Gefühle des anderen verletzt hat. Key: TRUE

result %>%
  mutate(score_statement1 = ifelse(statement1 == "false", 1, 0),
         score_statement2 = ifelse(statement2 == "true", 1, 0),
         score_statement3 = ifelse(statement3 == "false", 1, 0),
         score_statement4 = ifelse(statement4 == "true", 1, 0),
         score_statement5 = ifelse(statement5 == "false", 1, 0),
         score_statement6 = ifelse(statement6 == "false", 1, 0),
         score_statement7 = ifelse(statement7 == "false", 1, 0),
         score_statement8 = ifelse(statement8 == "true", 1, 0),
         score_statement9 = ifelse(statement9 == "true", 1, 0))%>%
  mutate(score_MCSD = rowSums(select(., starts_with("score_statement"))))-> result

```
# Lang. bio: Identify ingroup/ exposure to non-standard variety
## Prep
```{r lang.bio_prep, include=FALSE}

result %>%
  select(bilendi_id, bundesland, family_member1_response, family_member2_response, family_member3_response)%>%
  group_by(bilendi_id)->result_lang.bio

  distinct(result_lang.bio)->result_lang.bio

   str_trim(result_lang.bio$family_member1_response)
   str_trim(result_lang.bio$family_member2_response)
   
   keywords <-read_delim(here::here("data_processed", "keywords.csv"), col_names = TRUE, delim = ";")
   

# Rename columns for clarity
colnames(keywords) <- c("non.st.outgr", "non.st.ingr", "non.st.unspecific", "bilinguals", "st", "other")
```
## lang.bio: family member 1
```{r lang.bio1, include=FALSE}
# calculate distances of answers to target words and create categorical variable

# separate participants' response to family_member1 in several columns
result_lang.bio %>%
  separate(family_member1_response, sep = "\\s+|/|,", into = c("family_member1_response1a", "family_member1_response1b", "family_member1_response1c", "family_member1_response1d", "family_member1_response1e"), remove = F)%>%  separate(family_member2_response, sep = "\\s+|/|,", into = c("family_member2_response1a", "family_member2_response1b", "family_member2_response1c", "family_member2_response1d", "family_member2_response1e"), remove = F)->result_lang.bio

   str_trim(result_lang.bio$family_member1_response1a)
   str_trim(result_lang.bio$family_member1_response1b)
   str_trim(result_lang.bio$family_member1_response1c)
   str_trim(result_lang.bio$family_member1_response1d)
   str_trim(result_lang.bio$family_member1_response1e)
   
   str_trim(result_lang.bio$family_member2_response1a)
   str_trim(result_lang.bio$family_member2_response1b)
   str_trim(result_lang.bio$family_member2_response1c)
   str_trim(result_lang.bio$family_member2_response1d)
   str_trim(result_lang.bio$family_member2_response1e)

   
#family member1: Response A

# Create empty columns to store distances for each keyword
for (keyword_col in colnames(keywords)) {
  result_lang.bio[paste0("family1_response1a_distance_to_", keyword_col)] <- NA
}

# Loop through each participant's response
for (i in 1:nrow(result_lang.bio)) {
  response <- result_lang.bio$family_member1_response1a[i]
  
  # Loop through each keyword column
  for (keyword_col in colnames(keywords)) {
    # Calculate distances for each keyword in the column
    distances <- sapply(keywords[[keyword_col]], function(keyword) {
      stringdist::stringdist(response, keyword, method = "osa")
    })
    
    # Check for missing values in distances
    if (any(!is.na(distances))) {
      # Take the minimum distance
      min_distance <- min(distances, na.rm = TRUE)
    } else {
      # If all distances are NA, set min_distance to NA
      min_distance <- NA
    }
    
    # Assign the minimum distance to the corresponding column in the result dataset
    result_lang.bio[i, paste0("family1_response1a_distance_to_", keyword_col)] <- min_distance
  }
}


# family member1: Response B


##  Create empty columns to store distances for each keyword
for (keyword_col in colnames(keywords)) {
  result_lang.bio[paste0("family1_response1b_distance_to_", keyword_col)] <- NA
}

# Loop through each participant's response
for (i in 1:nrow(result_lang.bio)) {
  response <- result_lang.bio$family_member1_response1b[i]
  
  # Loop through each keyword column
  for (keyword_col in colnames(keywords)) {
    # Calculate distances for each keyword in the column
    distances <- sapply(keywords[[keyword_col]], function(keyword) {
      stringdist::stringdist(response, keyword, method = "osa")
    })
    
    # Check for missing values in distances
    if (any(!is.na(distances))) {
      # Take the minimum distance
      min_distance <- min(distances, na.rm = TRUE)
    } else {
      # If all distances are NA, set min_distance to NA
      min_distance <- NA
    }
    
    # Assign the minimum distance to the corresponding column in the result dataset
    result_lang.bio[i, paste0("family1_response1b_distance_to_", keyword_col)] <- min_distance
  }
}

#family member 1: Response C


##  Create empty columns to store distances for each keyword
for (keyword_col in colnames(keywords)) {
  result_lang.bio[paste0("family1_response1c_distance_to_", keyword_col)] <- NA
}

# Loop through each participant's response
for (i in 1:nrow(result_lang.bio)) {
  response <- result_lang.bio$family_member1_response1c[i]
  
  # Loop through each keyword column
  for (keyword_col in colnames(keywords)) {
    # Calculate distances for each keyword in the column
    distances <- sapply(keywords[[keyword_col]], function(keyword) {
      stringdist::stringdist(response, keyword, method = "osa")
    })
    
    # Check for missing values in distances
    if (any(!is.na(distances))) {
      # Take the minimum distance
      min_distance <- min(distances, na.rm = TRUE)
    } else {
      # If all distances are NA, set min_distance to NA
      min_distance <- NA
    }
    
    # Assign the minimum distance to the corresponding column in the result dataset
    result_lang.bio[i, paste0("family1_response1c_distance_to_", keyword_col)] <- min_distance
  }
}

#family member 1: Response D


##  Create empty columns to store distances for each keyword
for (keyword_col in colnames(keywords)) {
  result_lang.bio[paste0("family1_response1d_distance_to_", keyword_col)] <- NA
}

# Loop through each participant's response
for (i in 1:nrow(result_lang.bio)) {
  response <- result_lang.bio$family_member1_response1d[i]
  
  # Loop through each keyword column
  for (keyword_col in colnames(keywords)) {
    # Calculate distances for each keyword in the column
    distances <- sapply(keywords[[keyword_col]], function(keyword) {
      stringdist::stringdist(response, keyword, method = "osa")
    })
    
    # Check for missing values in distances
    if (any(!is.na(distances))) {
      # Take the minimum distance
      min_distance <- min(distances, na.rm = TRUE)
    } else {
      # If all distances are NA, set min_distance to NA
      min_distance <- NA
    }
    
    # Assign the minimum distance to the corresponding column in the result dataset
    result_lang.bio[i, paste0("family1_response1d_distance_to_", keyword_col)] <- min_distance
  }
}

#family member 1: Response E


##  Create empty columns to store distances for each keyword
for (keyword_col in colnames(keywords)) {
  result_lang.bio[paste0("family1_response1e_distance_to_", keyword_col)] <- NA
}

# Loop through each participant's response
for (i in 1:nrow(result_lang.bio)) {
  response <- result_lang.bio$family_member1_response1e[i]
  
  # Loop through each keyword column
  for (keyword_col in colnames(keywords)) {
    # Calculate distances for each keyword in the column
    distances <- sapply(keywords[[keyword_col]], function(keyword) {
      stringdist::stringdist(response, keyword, method = "osa")
    })
    
    # Check for missing values in distances
    if (any(!is.na(distances))) {
      # Take the minimum distance
      min_distance <- min(distances, na.rm = TRUE)
    } else {
      # If all distances are NA, set min_distance to NA
      min_distance <- NA
    }
    
    # Assign the minimum distance to the corresponding column in the result dataset
    result_lang.bio[i, paste0("family1_response1e_distance_to_", keyword_col)] <- min_distance
  }
}

# create final variable for family member 1 with min. distance categorisation

result_lang.bio %>%
  mutate(
    family_member1_cat.response = case_when(
      # Conditions for family_member1_response1a-e

family1_response1a_distance_to_non.st.ingr < 2 | family1_response1b_distance_to_non.st.ingr < 2 | family1_response1c_distance_to_non.st.ingr < 2 | family1_response1d_distance_to_non.st.ingr < 2 | family1_response1e_distance_to_non.st.ingr < 2 ~ "non_st.ingroup",

family1_response1a_distance_to_non.st.outgr < 2 | family1_response1b_distance_to_non.st.outgr < 2 | family1_response1c_distance_to_non.st.outgr < 2 | family1_response1d_distance_to_non.st.outgr< 2 | family1_response1e_distance_to_non.st.outgr < 2 ~ "non_st.outgroup",

family1_response1a_distance_to_bilinguals < 2 | family1_response1b_distance_to_bilinguals < 2 | family1_response1c_distance_to_bilinguals < 2 | family1_response1d_distance_to_bilinguals< 2 | family1_response1e_distance_to_bilinguals < 2 ~ "bilingual", 

#family1_response1a_distance_to_non.st.unspecific < 1 | family1_response1b_distance_to_non.st.unspecific < 1 | family1_response1c_distance_to_non.st.unspecific < 1 | family1_response1d_distance_to_non.st.unspecific < 1 | family1_response1e_distance_to_non.st.unspecific < 1 ~ "non.st.unspecific", 

family1_response1a_distance_to_st < 2 | family1_response1b_distance_to_st < 2 | family1_response1c_distance_to_st < 2 | family1_response1d_distance_to_st < 2 | family1_response1e_distance_to_st < 2 ~ "standard",

  family1_response1a_distance_to_other < 2 | family1_response1b_distance_to_other < 2 | family1_response1c_distance_to_other < 2 | family1_response1d_distance_to_other < 2 | family1_response1e_distance_to_other < 2 ~ "other",



      TRUE                      ~ "NA"
    )) -> result_lang.bio

result_lang.bio%>%
  select(
    bilendi_id, 
    family_member1_response1a,     family_member1_response1b, family_member1_response1c, 
    family_member1_response1d, family_member1_response1e,family_member1_cat.response) -> check_family1
```
## lang.bio: family member 2
```{r lang.bio_fam2, include=FALSE}
#family member2: Response A

# Create empty columns to store distances for each keyword
for (keyword_col in colnames(keywords)) {
  result_lang.bio[paste0("family1_response1a_distance_to_", keyword_col)] <- NA
}

# Loop through each participant's response
for (i in 1:nrow(result_lang.bio)) {
  response <- result_lang.bio$family_member2_response1a[i]
  
  # Loop through each keyword column
  for (keyword_col in colnames(keywords)) {
    # Calculate distances for each keyword in the column
    distances <- sapply(keywords[[keyword_col]], function(keyword) {
      stringdist::stringdist(response, keyword, method = "osa")
    })
    
    # Check for missing values in distances
    if (any(!is.na(distances))) {
      # Take the minimum distance
      min_distance <- min(distances, na.rm = TRUE)
    } else {
      # If all distances are NA, set min_distance to NA
      min_distance <- NA
    }
    
    # Assign the minimum distance to the corresponding column in the result dataset
    result_lang.bio[i, paste0("family2_response1a_distance_to_", keyword_col)] <- min_distance
  }
}


# family member2: Response B


##  Create empty columns to store distances for each keyword
for (keyword_col in colnames(keywords)) {
  result_lang.bio[paste0("family2_response1b_distance_to_", keyword_col)] <- NA
}

# Loop through each participant's response
for (i in 1:nrow(result_lang.bio)) {
  response <- result_lang.bio$family_member2_response1b[i]
  
  # Loop through each keyword column
  for (keyword_col in colnames(keywords)) {
    # Calculate distances for each keyword in the column
    distances <- sapply(keywords[[keyword_col]], function(keyword) {
      stringdist::stringdist(response, keyword, method = "osa")
    })
    
    # Check for missing values in distances
    if (any(!is.na(distances))) {
      # Take the minimum distance
      min_distance <- min(distances, na.rm = TRUE)
    } else {
      # If all distances are NA, set min_distance to NA
      min_distance <- NA
    }
    
    # Assign the minimum distance to the corresponding column in the result dataset
    result_lang.bio[i, paste0("family2_response1b_distance_to_", keyword_col)] <- min_distance
  }
}

#family member 2: Response C


##  Create empty columns to store distances for each keyword
for (keyword_col in colnames(keywords)) {
  result_lang.bio[paste0("family2_response1c_distance_to_", keyword_col)] <- NA
}

# Loop through each participant's response
for (i in 1:nrow(result_lang.bio)) {
  response <- result_lang.bio$family_member2_response1c[i]
  
  # Loop through each keyword column
  for (keyword_col in colnames(keywords)) {
    # Calculate distances for each keyword in the column
    distances <- sapply(keywords[[keyword_col]], function(keyword) {
      stringdist::stringdist(response, keyword, method = "osa")
    })
    
    # Check for missing values in distances
    if (any(!is.na(distances))) {
      # Take the minimum distance
      min_distance <- min(distances, na.rm = TRUE)
    } else {
      # If all distances are NA, set min_distance to NA
      min_distance <- NA
    }
    
    # Assign the minimum distance to the corresponding column in the result dataset
    result_lang.bio[i, paste0("family2_response1c_distance_to_", keyword_col)] <- min_distance
  }
}

#family member 2: Response D


##  Create empty columns to store distances for each keyword
for (keyword_col in colnames(keywords)) {
  result_lang.bio[paste0("family2_response1d_distance_to_", keyword_col)] <- NA
}

# Loop through each participant's response
for (i in 1:nrow(result_lang.bio)) {
  response <- result_lang.bio$family_member2_response1d[i]
  
  # Loop through each keyword column
  for (keyword_col in colnames(keywords)) {
    # Calculate distances for each keyword in the column
    distances <- sapply(keywords[[keyword_col]], function(keyword) {
      stringdist::stringdist(response, keyword, method = "osa")
    })
    
    # Check for missing values in distances
    if (any(!is.na(distances))) {
      # Take the minimum distance
      min_distance <- min(distances, na.rm = TRUE)
    } else {
      # If all distances are NA, set min_distance to NA
      min_distance <- NA
    }
    
    # Assign the minimum distance to the corresponding column in the result dataset
    result_lang.bio[i, paste0("family2_response1d_distance_to_", keyword_col)] <- min_distance
  }
}

#family member 2: Response E


##  Create empty columns to store distances for each keyword
for (keyword_col in colnames(keywords)) {
  result_lang.bio[paste0("family2_response1e_distance_to_", keyword_col)] <- NA
}

# Loop through each participant's response
for (i in 1:nrow(result_lang.bio)) {
  response <- result_lang.bio$family_member2_response1e[i]
  
  # Loop through each keyword column
  for (keyword_col in colnames(keywords)) {
    # Calculate distances for each keyword in the column
    distances <- sapply(keywords[[keyword_col]], function(keyword) {
      stringdist::stringdist(response, keyword, method = "osa")
    })
    
    # Check for missing values in distances
    if (any(!is.na(distances))) {
      # Take the minimum distance
      min_distance <- min(distances, na.rm = TRUE)
    } else {
      # If all distances are NA, set min_distance to NA
      min_distance <- NA
    }
    
    # Assign the minimum distance to the corresponding column in the result dataset
    result_lang.bio[i, paste0("family2_response1e_distance_to_", keyword_col)] <- min_distance
  }
}

# create final variable for family member 2 with min. distance categorisation

result_lang.bio %>%
  mutate(
    family_member2_cat.response = case_when(
      # Conditions for family_member2_response1a-e

family2_response1a_distance_to_non.st.ingr < 2 | family2_response1b_distance_to_non.st.ingr < 2 | family2_response1c_distance_to_non.st.ingr < 2 | family2_response1d_distance_to_non.st.ingr < 2 | family2_response1e_distance_to_non.st.ingr < 2 ~ "non_st.ingroup",

family2_response1a_distance_to_non.st.outgr < 2 | family2_response1b_distance_to_non.st.outgr < 2 | family2_response1c_distance_to_non.st.outgr < 2 | family2_response1d_distance_to_non.st.outgr< 2 | family2_response1e_distance_to_non.st.outgr < 2 ~ "non_st.outgroup",

family2_response1a_distance_to_bilinguals < 2 | family2_response1b_distance_to_bilinguals < 2 | family2_response1c_distance_to_bilinguals < 2 | family2_response1d_distance_to_bilinguals< 2 | family2_response1e_distance_to_bilinguals < 2 ~ "bilingual", 

#family2_response1a_distance_to_non.st.unspecific < 1 | family2_response1b_distance_to_non.st.unspecific < 1 | family2_response1c_distance_to_non.st.unspecific < 1 | family2_response1d_distance_to_non.st.unspecific < 1 | family2_response1e_distance_to_non.st.unspecific < 1 ~ "non.st.unspecific", 

family2_response1a_distance_to_st < 2 | family2_response1b_distance_to_st < 2 | family2_response1c_distance_to_st < 2 | family2_response1d_distance_to_st < 2 | family2_response1e_distance_to_st < 2 ~ "standard",

  family2_response1a_distance_to_other < 2 | family2_response1b_distance_to_other < 2 | family2_response1c_distance_to_other < 2 | family2_response1d_distance_to_other < 2 | family2_response1e_distance_to_other < 2 ~ "other",



      TRUE                      ~ "NA"
    )) -> result_lang.bio

result_lang.bio%>%
  select(
    bilendi_id, 
    family_member2_response1a,     family_member2_response1b, family_member2_response1c, 
    family_member2_response1d, family_member2_response1e,family_member2_cat.response) -> check_family2


# final data set 

result_lang.bio%>%
  select(bilendi_id, family_member1_response, family_member2_response, family_member1_cat.response, family_member2_cat.response)-> result_lang.bio
```
# Lang.bio
## integrate with main data set result
```{r lang.bio integrate, include=FALSE}

# join tables

left_join(result, result_lang.bio, by = c("bilendi_id", "family_member1_response", "family_member2_response"), relationship = "many-to-many")-> result
```
# descriptives
```{r descriptives, include=FALSE}


# Social desirability Scale
result %>%
  drop_na(score_MCSD)%>%
  summarise(
    mean(score_MCSD),
    sd(score_MCSD)
  ) -> sum_MCSD

# language bio
result%>%
  group_by(family_member1_cat.response)%>%
  summarise(n_distinct(bilendi_id))->pp_lang.bio_fam1

result%>%
  group_by(family_member2_cat.response)%>%
  summarise(n_distinct(bilendi_id))->pp_lang.bio_fam2

# sum_training
result%>%
  group_by(sum_training)%>%
  summarise(n_distinct(bilendi_id))->pp_sum_training

# education
result%>%
  group_by(education)%>%
  summarise(n_distinct(bilendi_id))->pp_education

# sum_education
result%>%
  group_by(sum_education)%>%
  summarise(n_distinct(bilendi_id))->pp_sum_education

# pp_gender

result%>%
  group_by(pp_gender)%>%
  summarise(n_distinct(bilendi_id))->pp_gender # two pp divers

# lang.bio fam

result%>%
  group_by(training)%>%
  summarise(n_distinct(bilendi_id))->pp_training
```
# Export data as csv

```{r export, include=FALSE}

write_delim(result, here("data_processed", "result_clean.csv"), col_names = TRUE, delim = ",")

```
