---
title: "All Data Analyses of AUDIO Swabian experiment: IAT & preselection"
author: "Judit Vari"
date: "20 2 2024"
output:
  html_document:
    toc: yes
---
# 1. Prep
## 1.1. session & all data
*load libraries*
```{r prep_library, include=FALSE}
library (dplyr)
library(broom)
library(ordinal)
library(lmerTest)
library(emmeans)
library(tidyverse)
library(sjPlot)
library(corrr)
library(ggcorrplot)
library(car)
library(report)
library (afex)
library(lme4)
library(optimx)
library(sjPlot)
library(ggeffects)
library(readr)
library(factoextra)
library(FactoMineR)
library(here)
#options(scipen=999)
```
*read cleaned data*
```{r read data, include=FALSE}
result <- read_delim(here("data_processed", "result_clean.csv"), col_names = TRUE, delim = ",")

result_preselect <- read_delim(here("data_processed", "result_preselect_clean.csv"), col_names = TRUE, delim = ",")
```
*assign classes*
```{r assign classes, include=FALSE}
result$ideology <- as.numeric(result$ideology)
result$populism1 <- as.numeric(result$populism1)
result$populism2 <- as.numeric(result$populism2)
result$populism3 <- as.numeric(result$populism3)
result$populism4 <- as.numeric(result$populism4)
result$age <- as.numeric(result$age)
result$bilendi_id <- as.numeric(result$bilendi_id)
result$trialcount <- as.numeric(result$trialcount)

result$charisma_lang_var<- as.factor(result$charisma_lang_var)
result$bundesland <- as.factor(result$bundesland)
result$education<- as.factor(result$education)
result$education_other<- as.factor(result$education_other)
result$employment_status<- as.factor(result$employment_status)
result$family_member1<- as.factor(result$family_member1)
result$family_member2<- as.factor(result$family_member2)
result$family_member3_<- as.factor(result$family_member3)
result$family_member1_other<- as.factor(result$family_member1_other)
result$family_member2_other<- as.factor(result$family_member2_other)
result$family_member3_other<- as.factor(result$family_member3_other)
result$pp_gender<- as.factor(result$pp_gender)
result$ideology_no_answer<- as.factor(result$ideology_no_answer)
result$ideology_unknown<- as.factor(result$ideology_unknown)
result$leadership_lang_var<- as.factor(result$leadership_lang_var)
result$moment<- as.factor(result$moment)
result$monthly_income<- as.factor(result$monthly_income)
result$speaker_gender<- as.factor(result$speaker_gender)
result$pp_gender<- as.factor(result$pp_gender)
result$statement1 <- as.factor(result$statement1)
result$statement2 <- as.factor(result$statement2)
result$statement3 <- as.factor(result$statement3)
result$statement4 <- as.factor(result$statement4)
result$statement5 <- as.factor(result$statement5)
result$statement6 <- as.factor(result$statement6)
result$statement7 <- as.factor(result$statement7)
result$statement8 <- as.factor(result$statement8)
result$statement9 <- as.factor(result$statement9)
result$stim_cat<- as.factor(result$stim_cat)
result$training<- as.factor(result$training)
result$training2<- as.factor(result$training2)
result$training_other<- as.factor(result$training_other)
result$training_other2<- as.factor(result$training_other2)
result$voting_behaviour<- as.factor(result$voting_behaviour)
result$voting_other<- as.factor(result$voting_other)
result$start_iat<- as.factor(result$start_iat)
result$sum_training<- as.factor(result$sum_training)
result$sum_education<- as.factor(result$sum_education)
result$family_member1_cat.response<- as.factor(result$family_member1_cat.response)
result$family_member2_cat.response<- as.factor(result$family_member2_cat.response)
```
## 1.2. Pre-selection of leadership attributes
*separate pre-selection phase data from IAT data*
Part of separate cleaned data set only with attributes:
variable "cat1_: leadership1" = „mit Charisma“
variable "cat2_: leadership2" = „ohne Charisma“
variables "cat1/2_list": Logging of final selection for leadership attributes of leadership category 1. Each attribute with associated rank
first 6 of variables "cat1/2_list" used for IAT.

Part of main cleaned data set containing meta data of selection process such as following 4 variables:
variable "count_ click_sequence": Count of sequences (1 sequence = 2 clicks:  1x selection of attribute +  1x allocation to place) min. 20 
variable "count_ check_selection": Count of calling check-up screen to revise pre-selection ((„Überprüfen Sie Ihre Auswahl…“) min. 1
variable "n_practice": Count of block no. of pre-selection practice (min: 0-3, max. 7)
variable "accuracy_practice_trial": Accuracy of block no. (max. 1 = 100%)

```{r preselection1, echo=FALSE}
result%>%
  filter(moment == "pre_selection")%>%
  select(bilendi_id, count_check_selection, count_click_sequence, accuracy_practice_trial, n_practice)%>%
  distinct()->data_pre
```
## 1.2. exclude practice blocks & filter speeders/ laggers
*create data set with only IAT data*
```{r prep_only_IAT_data, echo=FALSE}

result%>%
  filter(moment== "IAT")-> result
```
*include only four experimental blocks*
exclude practice blocks 1, 2 and 5 (after key switch) and include only experimental blocks 3,4,6,7 following Greenwld et al.
```{r prep_exp_blocks, echo=FALSE}

result%>%
  filter (blockno == 3 | blockno == 4  | blockno == 6 |blockno == 7)-> FourExpBlock
```
*exclude speeders & laggers*
exclude speeders: Greenwald et al: exclusion of entire data from subjects for whom more than 10% of trials have latencies faster than 300 ms
Experimental block 3 has 20 trial, block 4 has 40 trials, block 6 has 20 trials, block 7 has 40 trials
FourExpBlock = 120 trials 10% =  12, find pp whose RT is <300 ms for more than 12 trials
```{r prep_check_speed_lag, echo=FALSE}

FourExpBlock%>%
  group_by (bilendi_id)%>%
  summarise (n_distinct(trialcount))-> pp_trials 


FourExpBlock %>%
  group_by(bilendi_id) %>%
  summarize(rows_below_300 = sum(response_time < 300), mean(accuracy))-> FourBlock_pp_below_300 # 121 pp speeders!

```
*understand speeders*
examine two participants/ speeders
one_speeder1: 78 rows under 300, but acc 66 %
one_speeder2: 34 rows under 300 but acc. 60.525 -> speeder only in last experimental block
```{r prep_understand_speed_lag, echo=FALSE}

FourExpBlock%>%
  filter(bilendi_id== "264559562084358")%>%
  select(bilendi_id, sessionid, moment, blockno, trialcount, stimulus_ID, response_time, correct, age, pp_gender, meta_system_os )-> one_speeder1 


FourExpBlock%>%
  filter(bilendi_id== "265003370468468")%>%
  select(bilendi_id, sessionid, moment, blockno, trialcount, stimulus_ID, response_time, correct, age, pp_gender, meta_system_os )-> one_speeder2 

```
*exclude speeders & laggers*
decision:  Exclude participants with more than 10% fast (<300ms) trials & Exclude individual trials longer than 10,000 ms
do not exclude only specific experimental block (such as one_speeder2) or speeders with specific accuracy, rather follow Greenwald et al
```{r prep_exclude_speed_lagg, echo=FALSE}
FourExpBlock %>%
  group_by(bilendi_id) %>%
  filter(
    sum(response_time < 300) / n() <= 0.1,   
    !(response_time > 10000)                
  ) %>%
  ungroup()-> filtered_FourExpBlock
```
## 1.3. Descriptives IAT cleaning  
*How many participants excluded for speeders & laggers?*
Original no. participants
```{r prep_no._excl._speed_lag_original, echo=FALSE}
n_distinct(FourExpBlock$bilendi_id)
```
Cleaned data no. participants
```{r prep_no._excl._speed_lag_cleaned, echo=FALSE}
n_distinct(filtered_FourExpBlock$bilendi_id)
```
## 1.4. Treatment of incorrect trials

replaced Reaction times for error trials with: mean of correct responses plus 600 ms as penalty 
(other option in literature: the mean of correct responses in the block in which the error occurred plus a penalty of 2x the standard deviation of correct responses in the block in which the error occurred.)

```{r error trials, echo=FALSE}

filtered_FourExpBlock %>%
  group_by(bilendi_id, blockno) %>%
  mutate(mean_RT_corr_block = mean(response_time[correct == 1], na.rm = TRUE)) %>%
  mutate(penal_RTs = ifelse(correct == 0, mean_RT_corr_block + 600, response_time)) -> filtered_FourExpBlock

```
*write clean IAT data to csv*
```{r write clean IAT file, echo=FALSE}
write_delim(filtered_FourExpBlock, here::here("data_processed", "IAT_clean.csv"), col_names = T, delim = ",")
```
##1.5. Age related slowing  
*z-scores to address age-related slowing with data transformation (and not only age as co-variant)*

Hummert: Using the Implicit Association Test to Measure Age Differences in Implicit Social Cognitions
Faust, M. E., Balota, D. A., Spieler, D. H., & Ferraro, F. R. (1999).
Individual differences in information-processing rate and amount: Implications for group differences in response latency. Psychological Bulletin, 125, 777–799.

Several statistical transformations applied to response latencies to control for general age-related slowing. natural logs, proportion (dividing each individual’s mean latency on one task by the person’s mean latency on all tasks), task-level z scores (converting each individual’s mean latency on trials for one task into a z score on the basis of the person’s mean latency and standard deviation on all tasks), and trial-level z scores (using each person’s overall mean and standard deviation to convert each trial into a z score)

now: trial level z score: 

computed each participant’s mean and standard deviation across all trials all experimental blocks, use values used to convert pp's trial latencies into z scores

```{r age_standard, eval=FALSE, include=FALSE}
# z-score = (x-μ)/σ

# create z-scored RTs on trial level

filtered_FourExpBlock%>%
  group_by (bilendi_id)%>%
  mutate (z_scored_RTS1 = ((penal_RTs - mean(penal_RTs))/ sd(penal_RTs))) -> filtered_FourExpBlock
```
*Plots of IAT DVs*  
plots of DVs: response time (RTs) & penalised response time (error trials) & age related RTs*

```{r plots of RT DVs, eval=FALSE, include=FALSE}

# plot normal RTs
ggplot(filtered_FourExpBlock, aes(x=response_time)) +
   ggtitle("Plot of raw Response Times") +
           geom_density()-> plot_RT



# Plot RTs penalised

ggplot(filtered_FourExpBlock, aes(x=penal_RTs)) +
  ggtitle ("Plot of Penalised Reaction Times")+
  xlab("penalised RTs")+
         geom_density()-> plot_RT_penalised



# Plot age standardised RTs


ggplot(filtered_FourExpBlock, aes(x = z_scored_RTS1))+
  ggtitle("Plot of Age standardised Reaction times")+
  xlab("z_scored_RTs")+
  geom_density()->plot_filtered_FourExpBlock

plot_RT_penalised
plot_RT
plot_filtered_FourExpBlock

```

## 1.6. Create in- and outgroup subsets  

Separate ingroup from outgroup based on exposure to Swabian, outgroup consists of other non-standard, vernacular speakers, standard speakers and bilinguals, see data cleaning file. 

Continue with analyses of outgroup data set

```{r in_out_gr, include=FALSE}
filtered_FourExpBlock%>%
  filter(family_member1_cat.response == "non_st.ingroup" | family_member2_cat.response ==  "non_st.ingroup")-> Four_In

filtered_FourExpBlock%>%
  filter(family_member1_cat.response != "non_st.ingroup" & family_member2_cat.response != "non_st.ingroup" )-> Four_Out

```
*plots of in- and outgroup DVs*
```{r plots_in_out_gr_, include=FALSE}
ggplot(Four_Out, aes(x = penal_RTs))+
  ggtitle("Penalised Reaction Times in Outgroup")+
  geom_density()+ 
  xlab("Penalised Reaction Times")->plot_Four_Out_penal_RTs
plot_Four_Out_penal_RTs

ggplot(Four_In, aes(x = penal_RTs))+
  ggtitle("Penalised Reaction Times in Ingroup")+
    geom_density()+
  xlab("Penalised Reaction Times")->plot_Four_In_penal_RTs
plot_Four_Out_penal_RTs
plot_Four_In_penal_RTs
```
## 1.7. Prep political background  
#### 1.7.1. PCA
*PCA shows difference of populism 4 item in comparison to items populism 1, 2, 3*

Item populism 4 from elite dimension of Akkerman et al. 2014, populism 1-3 from populism dimension

```{r PCA_populism, echo=FALSE}
Four_Out%>%
  ungroup()%>%
  select(bilendi_id, populism1, populism2, populism3, populism4)-> PCA_pop_data


distinct (PCA_pop_data)-> PCA_pop_data 
pca_pop <- PCA(PCA_pop_data [, 2:5], scale.unit =TRUE, graph = TRUE) # option to include quali & quanti variables


fviz_eig(pca_pop) # scree plot variance explained dimensions, keep 2

pca_pop$var$coord

pca_pop <- PCA(PCA_pop_data [, 2:5], scale.unit =TRUE,
               graph = T, ncp = 2)

summary(pca_pop)

dimdesc(pca_pop, axes = c(1,2))



p_1a <- fviz_pca_var(pca_pop,geom = c("point","text"),
                  label = "var",
                  repel = TRUE,
                  col.var = "contrib",   # colour active variables according to their contribution to PCA axes
                  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
                  title= "PCA populism"
)

p_1a 

#ggsave(here("Output", "Four_Out_PCA_populism.jpg"))
```
*dimension reduction populism scales 1-4 after PCA*

```{r PCA_dim_reduction_populism, echo=FALSE}


populism_dim <- pca_pop$ind$coord [,1] 

as_tibble(populism_dim)->populism_dim

bind_cols(PCA_pop_data, populism_dim)->PCA_pop_data_final

left_join (Four_Out, PCA_pop_data_final, by = c("bilendi_id", "populism1", "populism2", "populism3", "populism4"))-> Four_Out # 69164 rows (Four_Out)
  
rename (Four_Out, populism_dim = value)-> Four_Out
```

*final dummy variables populism*
create 2 dummy variables for populism a) mean of populism scores items 1-3, but exclude pop 4 -> PCA shows very different b) use principal component 1 as dummy

```{r poplitical bckgr pop_dummies, echo=FALSE}
Four_Out %>%
  mutate(populism_all = rowMeans(across(c(populism1, populism2, populism3), as.numeric, .names = "mean_{col}"), na.rm = TRUE)) -> Four_Out

Four_In %>%
  mutate(populism_all = rowMeans(across(c(populism1, populism2, populism3), as.numeric, .names = "mean_{col}"), na.rm = TRUE)) -> Four_In


Four_Out%>%
  distinct(bilendi_id, populism_all)%>%
ggplot(aes(x=populism_all))+
  ggtitle("Plot of Populism Mean Scores") +
         geom_density()+
  ylab("no. of participants")+
  xlab("total score of populism items 1-3")-> Plot_sum_pop1
Plot_sum_pop1
#ggsave(here("Output", "Plot_sum_pop1.jpg"))


# add new populism dimension 1 of PCA
as.numeric(Four_Out$populism_dim)-> Four_Out$populism_dim

populism_dim%>%
   ggplot(aes(x=value))+
     ggtitle("Plot of Populism Dimension") +
     geom_density()+
  xlab ("Populism Prinincipal Component Scores")-> Plot_sum_pop2
Plot_sum_pop2
```
#### 1.7.2. Create subsets - high & low populism  
```{r populism_subsets, echo=FALSE}
Four_Out%>%
  ungroup()%>%
  summarise (sum(is.na(populism_all)))-> NA_no

anyNA(Four_Out$populism_all)


quantile(Four_Out$populism_all, na.rm = F) # 0%   1.000000;   25% 2.666667;      50%  3.333333;    75%  3.666667;   100% 5.000000 
    
Four_Out%>%
  filter(populism_all <= 3.333333)->Four_Out_low_pop

Four_Out%>%
  filter(populism_all >= 3.333333)->Four_Out_high_pop

Four_In%>%
  ungroup()%>%
  summarise (sum(is.na(populism_all)))-> NA_no

anyNA(Four_In$populism_all)


quantile(Four_In$populism_all, na.rm = F) # 0%   1.000000;   25% 2.666667;      50%  3.333333;    75%  3.666667;   100% 5.000000 


Four_In%>%
  filter(populism_all <= -0.03217982)->Four_In_low_pop

Four_In%>%
  filter(populism_all >= -0.03217982)->Four_In_high_pop


```
How many participants in subset high populism?
```{r populism_subsets_check_pp1, echo=FALSE}
n_distinct (Four_Out_high_pop$bilendi_id)

```
How many participants in subset low populism?
```{r populism_subsets_check_pp2, echo=FALSE}
n_distinct (Four_Out_low_pop$bilendi_id)
```
### 2.6. Prep SES  
#### Create subsets dummy variables education/ training
Create four data sets: high, middle, low as well as middle & low training/ education summary variables
```{r subset_SES_prep, echo=FALSE}
Four_Out%>%
  filter(sum_training == "high")-> Four_Out_high_train
Four_Out%>%
  filter(sum_training == "middle")-> Four_Out_middle_train
Four_Out%>%
  filter(sum_training == "low")-> Four_Out_low_train
Four_Out%>%
  filter(sum_training == "middle" | sum_training == "low")-> Four_Out_middle_low_train


Four_Out%>%
  filter(sum_education == "high")-> Four_Out_high_edu
Four_Out%>%
  filter(sum_education == "middle")-> Four_Out_middle_edu
Four_Out%>%
  filter(sum_education == "low")-> Four_Out_low_edu
Four_Out%>%
  filter(sum_education == "middle" | sum_education == "low")-> Four_Out_middle_low_edu
```
# 2. Descriptives
## 2.1. Leadership stimuli
### Top 6 attributes & consistency
Which attributes most often among top 6 for each leadership group?
How consistent is participants' ranking?
```{r preselection2, echo=FALSE}
result_preselect %>%
  group_by(Pre_select_type, Pre_select_Attribute) %>%
  summarise(rank_counts = sum(Pre_select_Rank <= 6)) %>%
  ungroup() %>%
  arrange(Pre_select_type, desc(rank_counts))->sum_attri_table

result_preselect %>%
  distinct(bilendi_id, Pre_select_type, Pre_select_Attribute, Pre_select_Rank)%>%
  group_by(Pre_select_type, Pre_select_Attribute) %>%
  summarise(mean_Rank = mean (Pre_select_Rank), median_Rank = median(Pre_select_Rank), RanK_standard_deviation = sd(Pre_select_Rank)) %>%
  arrange(Pre_select_type, desc(RanK_standard_deviation))->consistency_attri

# join tables

left_join(sum_attri_table,consistency_attri, by= c("Pre_select_type", "Pre_select_Attribute")) -> pre_select_attri

pre_select_attri

# Output summary table as csv

write_delim(pre_select_attri, here::here("output", "pre_select_attri.csv"), col_names = TRUE, delim = ",")

```
### Process of pre-selection of leadership attributes
Average clicks made for selection & average check of allocation
variable "count_ click_sequence": Count of sequences (1 sequence = 2 clicks:  1x selection of attribute +  1x allocation to place) min. 20 
variable "count_ check_selection": Count of calling check-up screen to revise pre-selection (Screen with „Überprüfen Sie Ihre Auswahl…“), value min. 1
```{r preslection3, echo=FALSE}

data_pre%>%
  distinct(bilendi_id, count_click_sequence, count_check_selection)%>%
  summarise(mean_clicks = mean (count_click_sequence), sd_click = sd (count_click_sequence), mean_check = mean (count_check_selection), sd_check = sd (count_check_selection))-> flow_pre_select

flow_pre_select
```
### Practice trials  
average no. of practice trials after selection of attributes & average accuracy in last practice trials
variable "n_practice": Count of block no. of pre-selection practice (min: 0-3, max. 7)
variable "accuracy_practice_trial": Accuracy of block no. (max. 1 = 100%)
```{r preselection4, echo=FALSE}
data_pre%>%
  distinct(bilendi_id, n_practice, accuracy_practice_trial)%>%
  summarise(mean_n_practice = mean (n_practice), sd_practice = sd (n_practice), mean_acc_pract_overall = mean (accuracy_practice_trial), sd_acc_pract_overall = sd (accuracy_practice_trial))-> flow_pre_practice

flow_pre_practice

data_pre %>%
  group_by(bilendi_id) %>%
  summarise(
    highest_block = max(n_practice),
    mean_accuracy_highest_block = mean(accuracy_practice_trial[n_practice == max(n_practice)])) %>%
  summarise(
    mean_accuracy_across_all = mean(mean_accuracy_highest_block), sd_accuracy_across_all = sd(mean_accuracy_highest_block))-> sum_acc_practice

sum_acc_practice
```
## 2.2. IAT data sets  
*No. of different stimuli presented*
how many stimuli presented to participants? -> 303! we had: lang. var stimuli: 6 speaker x 2 varieties  x 6 stimuli = 72 different stimuli PLUS leadership stimuli: 6 speakers x 2 varieties x 2 leadership cat x 6 stimuli = 144 different stimuli = 216, but since we had individual pre-selection, individuals vary what they picked as stimuli for leadership since not all participants picked the same 6 stimuli for leadership stimuli -> additional variation
```{r descriptives_stimuli_no, echo=FALSE}

n_distinct(filtered_FourExpBlock$bilendi_id)
```
*No. of participants in different data sets*
Ingroup data set
```{r descriptives_IAT_pp_no_all, echo=FALSE}
n_distinct(Four_In$bilendi_id)
```
Outgroup data set
```{r descriptives_IAT_pp_no_out, echo=FALSE}
n_distinct(Four_Out$bilendi_id)
```
*Participants' age*
age in all data set
```{r descriptives_IAT_age_all, echo=FALSE}
filtered_FourExpBlock %>%
drop_na(age)%>%
  summarise(mean(age), sd (age), min (age), max (age)) -> data_pp_age_result
data_pp_age_result

filtered_FourExpBlock%>%
  group_by(age)%>%
  summarise(participants = n_distinct(bilendi_id))-> All_data_age

All_data_age%>%
  ggplot() +
  ggtitle("age distribution in all data set") +
  geom_line(aes(x = age, y = participants))+
  xlab("age")+
  ylab ("count of participants")->sum_age_all
sum_age_all

```
age in outgroup data set
```{r descriptives_IAT_age_out, echo=FALSE}
Four_Out %>%
drop_na(age)%>%
  summarise(mean(age), sd (age), min (age), max (age)) -> data_pp_age_Out

Four_Out%>%
  group_by(age)%>%
  summarise(participants = n_distinct(bilendi_id))-> Four_Out_age

Four_Out_age%>%
  ggplot() +
  ggtitle("age distribution in outgroup data set") +
  geom_line(aes(x = age, y = participants))+
  xlab("age")+
  ylab ("count of participants")->sum_age_out
sum_age_out
```
age in ingroup data set
```{r descriptives_IAT_age_in, echo=FALSE}

Four_In %>%
drop_na(age)%>%
  summarise(mean(age), sd (age), min (age), max (age)) -> data_pp_age_In
data_pp_age_In

Four_In%>%
  group_by(age)%>%
  summarise(participants = n_distinct(bilendi_id))-> Four_In_age

Four_In_age%>%
  ggplot() +
  ggtitle("age distribution in ingroup data set") +
  geom_line(aes(x = age, y = participants))+
  xlab("age")+
  ylab ("count of participants")->sum_age_in
sum_age_in
```
write descriptive age to file
```{r descriptives_IAT_age_export, eval=FALSE, include=FALSE}
write.table(data_pp_age_Out, "data_pp_age_Out.csv")
```
*Participants' gender*
Gender distribution of participants in complete data set
```{r descriptives_IAT_gender_all, echo=FALSE}
filtered_FourExpBlock %>%
  group_by(pp_gender)%>%
  summarise(n_distinct(bilendi_id))-> data_pp_gender
data_pp_gender

filtered_FourExpBlock%>%
  group_by(pp_gender)%>%
  summarise(participants = n_distinct(bilendi_id))-> All_data_gender

All_data_gender%>%
  ggplot() +
  ggtitle("Plot of Gender Distribution in complete data set") +
  geom_col(aes(x = pp_gender, y = participants))+
  xlab("gender")+
  ylab ("count of participants")->sum_gender_all
sum_gender_all
```
Gender distribution of participants in outgroup data set
```{r descriptives_IAT_gender_out, echo=FALSE}
Four_Out %>%
  group_by(pp_gender)%>%
  summarise(n_distinct(bilendi_id))-> data_pp_gender_Out
data_pp_gender_Out

Four_Out%>%
  group_by(pp_gender)%>%
  summarise(participants = n_distinct(bilendi_id))-> Outgroup_gender

Outgroup_gender%>%
  ggplot() +
  ggtitle("Plot of Gender Distribution in Outgroup") +
  geom_col(aes(x = pp_gender, y = participants))+
  xlab("gender")+
  ylab ("count of participants")->sum_gender_out
sum_gender_out

```
Gender distribution of participants in ingroup data set
```{r descriptives_IAT_gender_in, echo=FALSE}
Four_In %>%
  group_by(pp_gender)%>%
  summarise(n_distinct(bilendi_id))-> data_pp_gender_In
data_pp_gender_In

Four_In%>%
  group_by(pp_gender)%>%
  summarise(participants = n_distinct(bilendi_id))-> Ingroup_gender

Ingroup_gender%>%
  ggplot() +
  ggtitle("Plot of Gender Distribution in Ingroup") +
  geom_col(aes(x = pp_gender, y = participants))+
  xlab("gender")+
  ylab ("count of participants")->sum_gender_in
sum_gender_in
```
*Participants' language biography*
exposure to language varieties by family member 1 & 2 in outgroup data set
```{r descriptives_IAT_lang_fam_bio, echo=FALSE}
Four_Out %>%
  group_by(family_member1_cat.response) %>%
  summarise(count = n_distinct(bilendi_id)) %>%
  arrange(count) -> data_pp_fam.bio1_out

data_pp_fam.bio1_out%>%
  ggplot() +
  ggtitle("Language variety of family member1 in Outgroup") +
  geom_col(aes(x = family_member1_cat.response, y = count))+
  xlab("language variety")+
  ylab ("count of participants")->sum_lang.bio1_out
sum_lang.bio1_out


Four_Out%>%group_by(family_member2_cat.response)%>%
  summarise(count = n_distinct(bilendi_id))%>% arrange(count)->data_pp_fam.bio2_out

data_pp_fam.bio2_out%>%
  ggplot() +
  ggtitle("Language variety of family member2 in Outgroup") +
  geom_col(aes(x = family_member2_cat.response, y = count))+
  xlab("language variety")+
  ylab ("count of participants")->sum_lang.bio2_out
sum_lang.bio2_out

bind_cols(data_pp_fam.bio1_out, data_pp_fam.bio2_out)-> data_pp_fam.bio_out
```
*Participants' higher education & professional training*
In all data set
```{r descriptives_IAT_sum_training_all_data, echo=FALSE}
filtered_FourExpBlock %>%
   group_by(sum_training)%>%
   summarise(count = n_distinct(bilendi_id)) -> data_pp_training
data_pp_training

data_pp_training%>%
  ggplot() +
  ggtitle("Higher education/training in all data") +
  geom_col(aes(x = sum_training, y = count))+
  xlab("Higher education/training")+
  ylab ("count of participants")->sum_training_all
sum_training_all

```
In outgroup data set
```{r descriptives_IAT_sum_training_out, echo=FALSE}
Four_Out %>%
   group_by(sum_training)%>%
   summarise(count = n_distinct(bilendi_id)) -> data_pp_training_Out
data_pp_training_Out

data_pp_training_Out%>%
  ggplot() +
  ggtitle("Higher education/training in Outgroup") +
  geom_col(aes(x = sum_training, y = count))+
  xlab("Higher Education/training")+
  ylab ("count of participants")->sum_training_out
sum_training_out
```
*Participants' secondary education*
In outgroup data set
```{r descriptives_IAT_sum_education_out, echo=FALSE}
# detailed variable education
Four_Out%>%
  group_by(education)%>%
summarise(n_distinct(bilendi_id))-> overview_education

# summary variable education

Four_Out %>%
   group_by(sum_education)%>%
   summarise(count = n_distinct(bilendi_id)) -> data_pp_education_Out
data_pp_education_Out

data_pp_education_Out%>%
  ggplot() +
  ggtitle("Secondary education in Outgroup") +
  geom_col(aes(x = sum_education, y = count))+
  xlab("Secondary Education")+
  ylab ("count of participants")->sum_education_out
sum_education_out
```
In all data set
```{r descriptives_IAT_sum_education_all, echo=FALSE}
filtered_FourExpBlock %>%
   group_by(sum_education)%>%
   summarise(count = n_distinct(bilendi_id)) -> data_pp_education
data_pp_education

data_pp_education%>%
  ggplot() +
  ggtitle("Secondary education in all data") +
  geom_col(aes(x = sum_education, y = count))+
  xlab("Secondary Education")+
  ylab ("count of participants")->sum_education_all
sum_education_all
```
In ingroup data set
```{r descriptives_IAT_sum_education_in, echo=FALSE}
Four_In %>%
   group_by(sum_education)%>%
   summarise(count = n_distinct(bilendi_id)) -> data_pp_education_in
data_pp_education_in

data_pp_education_in%>%
  ggplot() +
  ggtitle("Secondary education in Ingroup") +
  geom_col(aes(x = sum_education, y = count))+
  xlab("Secondary Education")+
  ylab ("count of participants")->sum_education_in
sum_education_in
```
*Participants' monthly income*
```{r descriptives_IAT_monthly_income, echo=FALSE}
Four_Out%>%
  group_by(monthly_income)%>%
summarise(n_distinct(bilendi_id))-> overview_monthly_income
```
*participants' political background*
**voting behaviour**
```{r poplitical bckgr descriptives_vot_behave, echo=FALSE}
Four_Out%>%
  group_by(voting_behaviour)%>%
  summarise(participants = n_distinct(bilendi_id))-> Four_Out_vot.behaviour

Four_Out_vot.behaviour%>%
  ggplot() +
  ggtitle("Plot of Voting Behaviour") +
  geom_col(aes(x = voting_behaviour, y = participants))+
  xlab("party")+
  ylab ("count of participants")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))->sum_voting_behaviour
sum_voting_behaviour

#ggsave(here("Output", "sum_voting_behaviour.jpg"))

```
**political ideology**
```{r poplitical bckgr ideology, echo=FALSE}
Four_Out%>%
  ungroup()%>%
  select (bilendi_id, voting_behaviour, ideology)%>%
  distinct(bilendi_id, voting_behaviour, ideology)->Four_Out_ideology

Four_Out_ideology%>%
summarise(mean(ideology), sd(ideology), min(ideology), max (ideology))-> Four_Out_sum_ideology

Four_Out_ideology%>%
ggplot(aes(x=ideology))+
  ggtitle("Plot of political ideology") +
         geom_bar()-> Plot_sum_ideology

Plot_sum_ideology
#ggsave(here("Output", "sum_ideology.jpg"))
```
**populism**
```{r poplitical bckgr populism, echo=FALSE}
Four_Out%>%
  drop_na (populism1)%>%
  drop_na (populism2)%>%
drop_na (populism3)%>%
drop_na (populism4)->Four_Out
Four_Out%>%
  ungroup()%>%
  summarise(mean(populism1), sd(populism1), min(populism1), max (populism1), mean(populism2), sd(populism2), min(populism2), max (populism2),  mean(populism3), sd(populism3), min(populism3), max (populism3),mean(populism4), sd(populism4), min(populism4), max (populism4))-> Four_Out_sum_populism
```
### scale all variables
```{r scale all, include=FALSE}
# data set: Four Out
Four_Out$ideology <- scale(Four_Out$ideology)
Four_Out$populism1 <- scale(Four_Out$populism1)
Four_Out$populism2 <- scale(Four_Out$populism2)
Four_Out$populism3 <- scale(Four_Out$populism3)
Four_Out$populism4 <- scale(Four_Out$populism4)
Four_Out$populism_all <- scale(Four_Out$populism_all)
Four_Out$populism_dim <- scale(Four_Out$populism_dim)
Four_Out$age <- scale(Four_Out$age)
Four_Out$penal_RTs <- scale(Four_Out$penal_RTs)
Four_Out$response_time <- scale(Four_Out$response_time)


# subset: Outgroup, high populism
Four_Out_high_pop$ideology <- scale(Four_Out_high_pop$ideology)
Four_Out_high_pop$populism1 <- scale(Four_Out_high_pop$populism1)
Four_Out_high_pop$populism2 <- scale(Four_Out_high_pop$populism2)
Four_Out_high_pop$populism3 <- scale(Four_Out_high_pop$populism3)
Four_Out_high_pop$populism4 <- scale(Four_Out_high_pop$populism4)
Four_Out_high_pop$populism_all <- scale(Four_Out_high_pop$populism_all)
Four_Out_high_pop$populism_dim <- scale(Four_Out_high_pop$populism_dim)
Four_Out_high_pop$age <- scale(Four_Out_high_pop$age)
Four_Out_high_pop$penal_RTs <- scale(Four_Out_high_pop$penal_RTs)
Four_Out_high_pop$response_time <- scale(Four_Out_high_pop$response_time)

# subset: Outgroup, low populism

Four_Out_low_pop$ideology <- scale(Four_Out_low_pop$ideology)
Four_Out_low_pop$populism1 <- scale(Four_Out_low_pop$populism1)
Four_Out_low_pop$populism2 <- scale(Four_Out_low_pop$populism2)
Four_Out_low_pop$populism3 <- scale(Four_Out_low_pop$populism3)
Four_Out_low_pop$populism4 <- scale(Four_Out_low_pop$populism4)
Four_Out_low_pop$populism_all <- scale(Four_Out_low_pop$populism_all)
Four_Out_low_pop$populism_dim <- scale(Four_Out_low_pop$populism_dim)
Four_Out_low_pop$age <- scale(Four_Out_low_pop$age)
Four_Out_low_pop$penal_RTs <- scale(Four_Out_low_pop$penal_RTs)
Four_Out_low_pop$response_time <- scale(Four_Out_low_pop$response_time)

# subset: Ingroup
Four_In
Four_In$ideology <- scale(Four_In$ideology)
Four_In$populism1 <- scale(Four_In$populism1)
Four_In$populism2 <- scale(Four_In$populism2)
Four_In$populism3 <- scale(Four_In$populism3)
Four_In$populism4 <- scale(Four_In$populism4)
Four_In$age <- scale(Four_In$age)
Four_In$penal_RTs <- scale(Four_In$penal_RTs)
Four_In$response_time <- scale(Four_In$response_time)
```
# 3. Analyses of outgroup data set
## 3.1. Correlation matrix
```{r corr._matrix, echo=FALSE}
as.numeric(Four_Out$age)->Four_Out$age
as.numeric(Four_Out$ideology)->Four_Out$ideology
as.numeric(Four_Out$populism1)->Four_Out$populism1
as.numeric(Four_Out$populism2)->Four_Out$populism2
as.numeric(Four_Out$populism3)->Four_Out$populism3
as.numeric(Four_Out$populism4)->Four_Out$populism4

drop_na(Four_Out, age)->Four_Out
drop_na(Four_Out, ideology)->Four_Out
drop_na(Four_Out, populism1)->Four_Out
drop_na(Four_Out, populism2)->Four_Out
drop_na(Four_Out, populism3)->Four_Out
drop_na(Four_Out, populism4)->Four_Out


Four_Out%>%
  ungroup()%>%
  select(penal_RTs, age, ideology, populism1, populism2, populism3, populism4)-> bckgr_poli

cor(bckgr_poli)->matrix_bckgr_poli

matrix_bckgr_poli
# Visualize correlations


ggcorrplot(matrix_bckgr_poli, 
           title = "Background variables", hc.order = TRUE, 
           type = "lower",lab = TRUE, lab_size = 2.5,  insig = "blank")->plot_corr_matrix
plot_corr_matrix

#ggsave(here ("output", "plot_corr_matrix.jpg"))
```
## 3.2. Impact language variety only
RQ: Do participants associate standard language variety more with charisma compared the vernacular variety? i.e. Are RTs faster when standard variety is mapped on the same key as charisma compared to when vernacular variety is mapped with charisma independent from study type (which mapping of language variety & charisma participants start with)?

Reaction time experiments need to take into account age related slowing. Two options to address age related slowing in model: 1) use z-scored RTs as DV 2) use age as co-variant

### 3.2.1. GLMs with age standardised RTs as DV

But: all models are singular fits, continue with age as co-variant
```{r glm_age_st_RTs, eval=FALSE, include=FALSE}

Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")
Four_Out$charisma_lang_var = relevel(Four_Out$charisma_lang_var, ref = "standard")

# lmer (z_scored_RTS1 ~ charisma_lang_var*start_iat + trialcount + stim_cat +(charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence

#lmer (z_scored_RTS1 ~ charisma_lang_var*start_iat + trialcount + stim_cat +(1|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence

#allFit(model1a) 
#summary (model1a)
#anova(model1a)
```
### 3.2.2 GLMS - age as covariant  
Max. model regarding experimental variables
```{r glm_outgroup_max.model, echo=FALSE}
Four_Out$start_iat = relevel(Four_Out$start_iat, ref = "standard-with Charisma")
Four_Out$charisma_lang_var = relevel(Four_Out$charisma_lang_var, ref = "standard")

#lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + stim_cat + age +(charisma_lang_var:start_iat|bilendi_id) +  (charisma_lang_var|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence -> simplify RE - structure

#lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + stim_cat + age +(charisma_lang_var|bilendi_id) +  (charisma_lang_var:start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence  -> simplify RE - structure
```
best fit model:
shows 2nd block (standard vernacular-with Charisma vs. vernacular standard-with Charisma) is significantly different
```{r glm_outgroup_best_fit_model1, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*start_iat +
        trialcount + stim_cat + age +
        (charisma_lang_var|bilendi_id) +
        (start_iat|stimulus_ID), 
      data = Four_Out,  REML = TRUE,
      lmerControl(optimizer="bobyqa",
                  optCtrl=list(maxfun=2e5))) -> model1a

summary (model1a)
anova(model1a)

emmeans(model1a, specs = pairwise ~ charisma_lang_var:start_iat)

plot_model(model1a, title = "Predicted values of reaction times", type = "pred", terms = c("charisma_lang_var", "start_iat")) +
  ylab ("reaction times")+
    xlab("lang. variety mapped with charisma")+
  labs(colour= str_wrap("Mapping of IAT start", width = 15))->plot_model1a
plot_model1a

#ggsave(here ("output", "int_lang.variety_start_iat.jpg"))
report(model1a)
```
change reference level to vernacular
```{r glm_outgroup_best_fit_model_diff_ref_level, echo=FALSE}
Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "vernacular-with Charisma")
Four_Out$charisma_lang_var = relevel(Four_Out$charisma_lang_var, ref = "vernacular")

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var  + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1b
summary(model1b)
```
## 3.3. Language variety plus foci 
### 3.3.1. Age
explore age related slowing: present in general but not in interaction with study type variable "start_iat" & "charisma_lang_var".
```{r glm_age, echo=FALSE}
# Max. Model: age

Four_Out$charisma_lang_var = relevel(Four_Out$charisma_lang_var , ref = "standard")
Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")

#lmer (penal_RTs ~ charisma_lang_var*start_iat*age + trialcount + leadership_lang_var + speaker_gender*pp_gender + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model3a
#summary (model3a)
#anova(model3a) # drop  3-way int- "charisma_lang_var:start_iat:age" & "speaker_gender:pp_gender" non-sign

# lmer (penal_RTs ~ charisma_lang_var:start_iat + charisma_lang_var:age + trialcount + leadership_lang_var + speaker_gender + pp_gender + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model3a
# summary (model3a)
# anova(model3a)# drop "pp_gender"

lmer (penal_RTs ~ charisma_lang_var:start_iat + charisma_lang_var:age + trialcount + leadership_lang_var + speaker_gender + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model3a
summary (model3a)
anova(model3a)

plot_model(model3a, title = "Predicted values of RT", type = "pred", terms = "age")+
  ylab ("RT")+
    xlab("age")->plot_age
plot_age 


emmeans(model3a, specs = pairwise ~ charisma_lang_var:start_iat)
emtrends(model3a, "charisma_lang_var", var = "age")

plot_model(model3a, title = "Predicted values of RT", type = "pred", terms = c("age", "charisma_lang_var")) +
  ylab ("Reaction times")+
    xlab("age")+
labs(colour= str_wrap("Lang. variety mapped with Charisma", width = 15)) ->plot_int_age
plot_int_age # why are there no confidence intervals

#ggsave(here("output", "age_slow_effect.jpg")) 
```
### 3.3.2 Family language  
```{r glm_outgroup_family.bio, echo=FALSE}
Four_Out$family_member1_cat.response = relevel(Four_Out$family_member1_cat.response , ref = "standard")

lmer (penal_RTs ~ charisma_lang_var*start_iat*family_member1_cat.response + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model2a_fam.Bio
summary(model2a_fam.Bio)
anova(model2a_fam.Bio)

Four_Out$family_member2_cat.response = relevel(Four_Out$family_member2_cat.response , ref = "standard")

lmer (penal_RTs ~  charisma_lang_var*start_iat*family_member2_cat.response + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model2b_fam.Bio
summary(model2b_fam.Bio) 
anova (model2b_fam.Bio)


plot_model(model2a_fam.Bio, title = "Predicted Values of RT", type = "pred", terms =  c("charisma_lang_var", "start_iat", "family_member1_cat.response"), dodge =0.9) +
   theme(plot.margin = margin(0.5, .5, .5, .5, "cm")) +    theme(axis.text.x = element_text(angle = 15, hjust = 1))+
  ylab ("RT")+
  xlab("lang. variety mapped with charisma") ->plot_fam1.Bio
plot_fam1.Bio
#ggsave(here ("output", "int_fam.Bio1.jpg"))

plot_model(model2b_fam.Bio, title = "Predicted values of reaction times", type = "pred", terms = c("charisma_lang_var", "start_iat", "family_member2_cat.response"), dodge =0.9)+
  ylab ("RT")+
  xlab("lang. variety mapped with charisma")+
  theme(axis.text.x = element_text(angle = 15, hjust = 1)) ->plot_fam2.Bio
plot_fam2.Bio

#ggsave(here ("output", "int_fam.Bio2.jpg"))
```
### 3.3.3 Region
no impact of region/ Bundesland
```{r glm_outgroup_region, echo=FALSE}
lmer (penal_RTs ~  charisma_lang_var*start_iat*bundesland + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model_region
summary(model_region) 
anova (model_region)
```
### 3.3.4 Focus gender
#### Speaker gender
no significant difference between female vernacular - male vernacular & female standard - male standard
```{r glm_outgroup_speak_gender, echo=FALSE}
#as.numeric(scale(Four_Out$penal_RTs)) -> Four_Out$penal_RTs
#as.numeric(scale(Four_Out$age)) -> Four_Out$age

Four_Out%>%
  drop_na(pp_gender)%>%
  filter (pp_gender != "divers")->Four_Out_gend

Four_Out_gend$speaker_gender = relevel(Four_Out_gend$speaker_gender , ref = "female")
Four_Out_gend$pp_gender = relevel(Four_Out_gend$pp_gender , ref = "female")

lmer (penal_RTs ~ charisma_lang_var*start_iat*speaker_gender + trialcount + leadership_lang_var + stim_cat + age + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_gend,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model3a
summary (model3a)
anova(model3a)
emmeans(model3a, specs = pairwise ~ charisma_lang_var:speaker_gender) 

plot_model(model3a, title = "Predicted values of RTs", type = "pred", terms = c("speaker_gender", "charisma_lang_var")) +
  ylab ("RT") + 
  xlab("gender of stimuli speaker")+
 labs(colour=str_wrap("Lang. variety mapped with charisma", width= 15)) ->plot_int_speak_gender
plot_int_speak_gender


#ggsave(here("Output", "Plot_charilangXSpeaker_Gender.jpg"))
```
#### Participant gender  
not significant difference between female vernacular - male vernacular & female standard - male standard
```{r glm_outgroup_pp_gender, echo=FALSE}
lmer (penal_RTs ~ charisma_lang_var*start_iat*pp_gender  + trialcount + leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_gend,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model3c
summary (model3c)
anova (model3c)
emmeans(model3c, specs = pairwise ~ charisma_lang_var:start_iat:pp_gender)

plot_model(model3c, title = "Predicted values of RTs", type = "pred", terms = c("pp_gender", "charisma_lang_var")) +
  ylab ("Reaction times") + 
  xlab ("participant gender")+
  labs(colour= str_wrap("Lang. variety mapped with charisma", width = 15))->plot_pp_gender
plot_pp_gender

#ggsave(here("Output", "charilangXstartXpp_Gender.jpg"))
```
#### Interaction participant & speaker gender
```{r glm_pp_speak_gender, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*pp_gender*speaker_gender  + start_iat + trialcount + leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_gend,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model3d
summary (model3d)
anova (model3d)
emmeans(model3d, specs = pairwise ~ charisma_lang_var:speaker_gender:pp_gender)

plot_model(model3d, type = "est", show.values = T, digits = 2, dot.size = 2, show.p = T, value.offset = 0.5, value.size = 2.5, show.intercept =T, title = "Predicting reaction time", wrap.title = 10, wrap.labels = 15) ->plot_est_ppgenderXspeak_gender
plot_est_ppgenderXspeak_gender

#ggsave(here("Output", "estimates_charilangXspeak_genderXpp_Gender.jpg"))


plot_model(model3d, type = "pred", terms = c("speaker_gender", "charisma_lang_var", "pp_gender"), dodge =.5, facet_grid()) +
   theme(plot.margin = margin(1, 1, 1, 1, "cm")) +    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylab ("Reaction times") + 
  xlab ("speaker gender")+
  labs(colour= str_wrap("Lang. variety mapped with charisma", width = 12))+
  labs(title = "Predicted values of RTs", subtitle = "Participant gender")  ->plot_speak_genderXpp_gender
plot_speak_genderXpp_gender

#ggsave(here("Output", "charilangXspeak_genderXpp_Gender.jpg"))
```
#### Subset analyses gender  
##### female speaker  
comparisons of 2nd block not significant
```{r outgroup_gender_subset_fem, echo=FALSE}
Four_Out_gend%>%
  filter(speaker_gender == "female")->Four_Out_fem

lmer (penal_RTs ~ charisma_lang_var*start_iat*pp_gender + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_fem,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model4a
summary (model4a)
anova(model4a)
emmeans(model4a, specs = pairwise ~ charisma_lang_var:start_iat)

lmer (penal_RTs ~ charisma_lang_var*pp_gender + start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_fem,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model4b
summary (model4b)
anova(model4b)
emmeans(model4b, specs = pairwise ~ charisma_lang_var:pp_gender)

plot_model(model4a, title = , type = "pred", terms = c("charisma_lang_var", "start_iat", "pp_gender"), dodge =.5) +
   theme(plot.margin = margin(1, 1, 1, 1, "cm")) +    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylab ("RT")+
xlab("Lang. variety mapped with charisma")+
  labs(colour="started IAT with mapping")+
  labs(title = "Predicted values of RT for speaker gender female", subtitle = "Grouped by participant gender")  ->Plot_Four_Out_fem1
Plot_Four_Out_fem1
#ggsave(here("Output", "Four_Out_fem1.jpg"))

plot_model(model4b, title = "Predicted values of RT for speaker gender female", type = "pred", term = c("charisma_lang_var", "start_iat")) +
  ylab ("RT")+
xlab("Lang. variety mapped with charisma")+
  labs(colour="started IAT with mapping")->Plot_Four_Out_fem2
Plot_Four_Out_fem2
#ggsave(here("Output", "Four_Out_fem2.jpg"))
```
##### male speakers  
language variety impact between 2nd blocks of different study types only approaching significance 
```{r outgroup_gender_subset_male, echo=FALSE}
Four_Out_gend%>%
  filter (speaker_gender == "male")->Four_Out_male


lmer (penal_RTs ~ charisma_lang_var*start_iat*pp_gender + trialcount + age+ leadership_lang_var +  + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_male,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model4c
summary (model4c)
anova(model4c)

lmer (penal_RTs ~ charisma_lang_var*pp_gender + trialcount + age+ leadership_lang_var +  + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_male,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model4d
summary (model4d)
anova(model4d)

plot_model(model4c, title = , type = "pred", terms = c("charisma_lang_var", "start_iat", "pp_gender"), dodge =.5) +
   theme(plot.margin = margin(1, 1, 1, 1, "cm")) +    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylab ("RT")+
xlab("Lang. variety mapped with charisma")+
  labs(colour="started IAT with mapping")+
  labs(title = "Predicted values of RT for speaker gender male", subtitle = "Grouped by participant gender")  ->Plot_Four_Out_male1
Plot_Four_Out_male1
#ggsave(here("Output", "Four_Out_male1.jpg"))

plot_model(model4d, title = "Predicted values of RT for speaker gender male", type = "pred", term = c("charisma_lang_var", "pp_gender")) +
  ylab ("RT")+
xlab("Lang. variety mapped with charisma")->Plot_Four_Out_male2
Plot_Four_Out_male2
#ggsave(here("Output", "Four_Out_male2.jpg"))
```
## 3.4. Language variety & political background
RQ: Do variables of participants' political background mediate how language variety impacts on reaction times?
### 3.4.1. GLMs: Max model
```{r poplitical bckgr max model, echo=FALSE}
# Max. Model all political background measures

Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + stim_cat + age+ leadership_lang_var + populism_dim:charisma_lang_var + ideology:charisma_lang_var + voting_behaviour:charisma_lang_var  + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5
summary (model5)
anova(model5)
```
### 3.4.2. Populism  
#### GLMs all data
*no impact of populism measure, populism_all, populism_dim*
First, using variable populism_all (mean of populism questionnaire items 1-3)
```{r poplitical bckgr pop_mean_all, echo=FALSE}
Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")
Four_Out$charisma_lang_var = relevel(Four_Out$charisma_lang_var, ref = "standard")

#lmer (penal_RTs ~ charisma_lang_var*start_iat*populism_all + trialcount + age+ leadership_lang_var 
       # + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
#summary (model5a)
#anova(model5a) # 3 way interact. non-sign. -> drop

lmer (penal_RTs ~ charisma_lang_var*populism_all + start_iat + trialcount + age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
summary (model5a)
anova(model5a)
```
Second, using variable populism_dim (dimension 1 of Populism PCA)
```{r poplitical bckgr pop_dim, echo=FALSE}

#lmer (penal_RTs ~ charisma_lang_var*start_iat*populism_dim + trialcount + age+ leadership_lang_var 
       # + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
#summary (model5a) 
#anova(model5a)  # 3 way interact. non-sign.

lmer (penal_RTs ~ charisma_lang_var*populism_dim + trialcount + start_iat+ age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
summary (model5a)
anova(model5a)

# using populism 4 measure (more elitist item compared to populism1-3)

as.numeric(scale(Four_Out$populism4))->Four_Out$populism4

lmer (penal_RTs ~ charisma_lang_var*start_iat*populism4 + trialcount +age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5c
summary (model5c)
anova(model5c)
```
#### Populism subset analyes
difference between 2nd blocks (charisma_lang_var*start_iat), i.e.impact of vernacular when starting with standard-with Charisma vs. impact of standard variety when starting with vernacular-with Charisma) is significant in low populism subset but not significant in high populism subset
```{r pop_subset analyses, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*start_iat+
        trialcount + age+ leadership_lang_var +
        (charisma_lang_var|bilendi_id) + 
        (start_iat|stimulus_ID), 
      data = Four_In_high_pop, REML = T,
      lmerControl(optimizer="bobyqa",
                  optCtrl=list(maxfun=2e5))) -> model_pop_high
summary (model_pop_high)
anova(model_pop_high)
emmeans(model_pop_high, specs = pairwise ~ charisma_lang_var:start_iat)

lmer (penal_RTs ~ charisma_lang_var*start_iat+
        trialcount + age+ leadership_lang_var 
        +
        (charisma_lang_var|bilendi_id) +
        (start_iat|stimulus_ID), 
      data = Four_In_low_pop,  REML = T,
      lmerControl(optimizer="bobyqa",
                  optCtrl=list(maxfun=2e5))) -> model_pop_low
summary (model_pop_low)
anova(model_pop_low)
emmeans(model_pop_low, specs = pairwise ~ charisma_lang_var:start_iat) 

plot_model(model_pop_high, type = "int") +
  ylab ("RT")+
    xlab("lang. variety mapped with charisma")+
  labs ( title = "Predicted values of RT", subtitle = "high populism group")+
  labs(colour="started IAT with mapping")->plot_model_pop_high
plot_model_pop_high
#ggsave(here("Output", "Subset_pop_high_lang.varXstart.jpg"))



plot_model(model_pop_low, type = "int") +
   ylab ("RT")+
    xlab("lang. variety mapped with Charisma")+
  labs ( title = "Predicted values of RT", subtitle = "low populism group")+labs(colour="started IAT with mapping")->plot_model_pop_low
plot_model_pop_low
#ggsave(here("Output", "Subset_pop_low_lang.varXstart.jpg"))


plot_model_pop_low

plot_model_pop_high
```
#### Populism & gender
Does gender impact on how populism mediates the effect of language variety on RTs?

##### outgroup data
*no impact of stimuli speaker/participant gender in complete data set with neither populism measure*
First, variable populism_all (mean of populism items 1-3)
```{r populism_all_gender, echo=FALSE}
lmer (penal_RTs ~ charisma_lang_var*populism_all*speaker_gender + start_iat + trialcount + age+ # pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5b_gender
summary (model5b_gender)
anova(model5b_gender)
```
Second, variable populism_dim (first PC dimension reduction)
```{r populism_dim_gender, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*populism_dim *speaker_gender + start_iat + trialcount + age+ # pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5d_gender
summary (model5d_gender)
anova(model5d_gender)
```
##### Subset analyses  
###### low populism & speaker gender 
no impact of gender stimuli speaker in populism subset (low) & populism_all/ populism_dim
```{r low_pop_subset speaker_gender, echo=FALSE}
lmer (penal_RTs ~ charisma_lang_var*populism_all*speaker_gender + start_iat + trialcount + age+ pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_low_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5alowPop
summary (model5alowPop)
anova(model5alowPop)

lmer (penal_RTs ~ charisma_lang_var*populism_dim*speaker_gender + start_iat + trialcount + age+ pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_low_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5blowPop
summary (model5blowPop)
anova(model5blowPop)
```
###### low populism & participant gender  
no impact of participant gender in populism subset (low) & populism_all/ populism_dim
```{r low_pop_subset pp_gender, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*populism_all*pp_gender + start_iat + trialcount + age+ 
     speaker_gender   + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_low_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5alowPop
summary (model5alowPop)
anova(model5alowPop)

lmer (penal_RTs ~ charisma_lang_var*populism_dim*pp_gender + start_iat + trialcount + age+ 
     speaker_gender   + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_low_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5blowPop
summary (model5blowPop)
anova(model5blowPop)
```
###### high populism & speaker gender  
no impact of gender stimuli speaker in populism subset (high) & populism_all/ populism_dim
```{r high_pop_subset speaker_gender, echo=FALSE}
lmer (penal_RTs ~ charisma_lang_var*populism_all*speaker_gender + start_iat + trialcount + age+ pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_high_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5highPop
summary (model5highPop)
anova(model5highPop)


lmer (penal_RTs ~ charisma_lang_var*populism_dim*speaker_gender + start_iat + trialcount + age+ pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_high_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5highPop
summary (model5highPop)
anova(model5highPop)
```
###### high populism & participant gender
no impact of participant gender in populism subset (high) & populism_all/ populism_dim

```{r high_pop_subset pp_gender, echo=FALSE}
lmer (penal_RTs ~ charisma_lang_var*populism_all*pp_gender + start_iat + trialcount + age+ 
     speaker_gender   + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_high_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5highPop
summary (model5highPop)
anova(model5highPop)

lmer (penal_RTs ~ charisma_lang_var*populism_dim*pp_gender + start_iat + trialcount + age+ 
     speaker_gender   + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_high_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5highPop
summary (model5highPop)
anova(model5highPop)
```
#### Populism & region 
##### general GLMs 
Simple effects: Sachsen as well as Brandenburg  diff. to ref.level (BaWü) in Standard variety & populism scale  
```{r pop_region, echo=FALSE}
as.numeric(Four_Out$populism_all)->Four_Out$populism_all
lmer (penal_RTs ~ charisma_lang_var:populism_all:bundesland + trialcount  + age+ leadership_lang_var + start_iat + (charisma_lang_var|bilendi_id) +  (populism_all|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_reg_pop1
summary (model_reg_pop1)
anova(model_reg_pop1)


lmer (penal_RTs ~ charisma_lang_var:populism_dim:bundesland + trialcount  + age+ leadership_lang_var + start_iat + (charisma_lang_var|bilendi_id) +  (populism_all|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_reg_pop2
summary (model_reg_pop2)
anova(model_reg_pop2)

## Plot

ggpredict(model_reg_pop1, terms = c("populism_all", "charisma_lang_var", "bundesland"), type = "fe") -> model_reg_pred
model_reg_pred

summary(model_reg_pred)
  
model_reg_pred %>% ggplot(aes(x, predicted, color = group, linetype = group)) +
  geom_smooth() +
  #geom_errorbar(ymin = model_reg_pred$conf.low, ymax = model_reg_pred$conf.high,
                #size = 0.4, width = 0.2) +
  facet_wrap(~facet)+
  #ylim (2, 2)+
  ylab("Predicted Values of RT") + 
  #xlim (2, 2)+ 
xlab("Populism Score")->
populism_regio
populism_regio
```
##### subset analyses - low populism
```{r pop_region_subset_low, echo=FALSE}
lmer (penal_RTs ~ charisma_lang_var:bundesland + trialcount  + age+ leadership_lang_var + start_iat + (charisma_lang_var|bilendi_id) +  (populism_all|stimulus_ID), data = Four_Out_low_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_reg_pop_low
summary (model_reg_pop_low)
anova(model_reg_pop_low)
```
#####subset analyses - high populism
simple effect for Brandenburg standard compared to ref.level (BaWü) and Brandenburg compared standard vs. vernacular (positive slope)-> participants slower in trials with vernacular & charisma compared to Standard in Brandenburg
```{r pop_region_subset_high, echo=FALSE}
lmer (penal_RTs ~ charisma_lang_var:bundesland + trialcount  + age+ leadership_lang_var + start_iat + (charisma_lang_var|bilendi_id) +  (populism_all|stimulus_ID), data = Four_Out_high_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_reg_pop_high
summary (model_reg_pop_high)
anova(model_reg_pop_high)
```
### 3.4.3. Political ideology
#### General
```{r political ideology, echo=FALSE}

#as.numeric(scale(Four_Out$ideology))->Four_Out$ideology

lmer (penal_RTs ~ charisma_lang_var*start_iat*ideology + trialcount  + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5c
summary (model5c)
anova(model5c)
emtrends(model5c, ~ charisma_lang_var | start_iat, var = "ideology")

plot_model(model5c, type = "pred", terms = c("ideology", "charisma_lang_var",  "start_iat")) +
   ylab ("RT")+
    xlab ("political ideoloy left - right")+
  labs(colour="lang. variety mapped with Charisma")+
  labs ( title = "Predicted values of RT", subtitle = "grouped by started IAT with mapping")->plot_ideol_lang.varXstart
  
plot_ideol_lang.varXstart

#ggsave(here("Output", "plot_ideol_lang.varXstart.jpg"))

```
#### Political ideology & gender
```{r political bckgr ideology gender, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*ideology*speaker_gender + start_iat + trialcount + age+ pp_gender + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5d
summary (model5d)
anova(model5d)
```
### 3.4.4. Voting behaviour
Simple effects in contrasts lang. variety level vernacular and Grün vs. LINKE, CDU/CSU vs. LINKE, AfD vs.LINKe approaching significance
```{r voting_behaviour, echo=FALSE}

Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "AfD")

lmer (penal_RTs ~ charisma_lang_var*start_iat*voting_behaviour + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5AfD
summary (model5AfD)


Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "FDP")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5FDP
summary (model5FDP) 

Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "GRüNE")

lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5grün
summary (model5grün)



Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "CDU/CSU")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5CDU
summary (model5CDU)

Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "DIE LINKE")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5links
summary (model5links)
anova(model5links)
emmeans(model5links, specs = pairwise ~ charisma_lang_var:start_iat:voting_behaviour)

plot_model(model5links, title = "Predicted Values of RT - Die LINKE", type = "pred", terms = c("charisma_lang_var", "start_iat")) +
  ylab ("RT")+
xlab("Lang. variety mapped with charisma")+
  labs(colour="started IAT with mapping") ->plot_LINKE_lang.varXstart
plot_LINKE_lang.varXstart
#ggsave(here("Output", "plot_LINKE_lang.varXstart.jpg"))

plot_model(model5links, type = "pred", terms = c("charisma_lang_var", "start_iat", "voting_behaviour")) +
  ggtitle("Predicted Values of RT - ref. die LINKE", subtitle = "Grouped by voting behaviour")+
  ylab ("RT")+
xlab("Lang. variety mapped with charisma")+
  labs(colour="started IAT with mapping") ->plot_pol.behaviour_lang.varXstart
plot_LINKE_lang.varXstart
#ggsave(here("Output", "plot_pol.behav_lang.varXstart.jpg"))


Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "SPD")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5SPD
summary (model5SPD)


Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "Nichtwähler")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5nonVot
summary (model5nonVot)

# voting_other

Four_Out%>%
  group_by(voting_other)%>%
summarise(n_distinct(bilendi_id))-> overview_voting_other # Frei Wähler top, but overall only 6 pp
```
## 3.5. Impact of language variety & SES
RQ: Do variables of participants' SES mediate how language variety impacts on reaction times?
```{r glm_outgroup_SES_measures1, echo=FALSE}

as.factor(Four_Out$education)-> Four_Out$education
as.factor(Four_Out$employment_status)-> Four_Out$employment_status
as.factor(Four_Out$monthly_income)-> Four_Out$monthly_income
as.factor(Four_Out$training)-> Four_Out$training
as.factor(Four_Out$training2)-> Four_Out$training2
as.factor(Four_Out$training_other)-> Four_Out$training_other
as.factor(Four_Out$training_other2)-> Four_Out$training_other2
as.factor(Four_Out$sum_training)-> Four_Out$sum_training
as.factor(Four_Out$sum_education)-> Four_Out$sum_education

```
### 3.5.1. Max.model
simple effects for charisma_lang_varvernacular:education Realschulabschluss, Mittlere Reife, Fachschulreife oder Abschluss der polytechnischen Oberschule 10. Klasse, as well as Azubi/SchülerIn
```{r glm_outgroup_SES_measures_max, echo=FALSE}
Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")
Four_Out$charisma_lang_var = relevel(Four_Out$charisma_lang_var , ref = "standard")

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + stim_cat + 
        #age+ 
        leadership_lang_var + sum_education:charisma_lang_var + employment_status:charisma_lang_var + sum_training:charisma_lang_var  + monthly_income:charisma_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6
summary (model6) 
anova(model6)
```
### 3.5.2. Focus income
```{r glm_outgroup_SES_focus_income, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*start_iat*monthly_income  + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6d
summary (model6d)
anova(model6d)
```
### 3.5.2. Focus education
```{r glm_outgroup_SES_focus education, echo=FALSE}
unique(Four_Out$education)
Four_Out$education = relevel(Four_Out$education , ref = "Abitur bzw. erweiterte Oberschule mit Abschluss 12. Klasse (Hochschulreife)")


lmer (penal_RTs ~ charisma_lang_var*start_iat*education + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6c
summary (model6c)
anova(model6c)

Four_Out$education = relevel(Four_Out$education , ref = "Hauptschulabschluss, Volksschulabschluss, Abschluss der polytechnischen Oberschule 8. oder 9. Klasse")
lmer (penal_RTs ~ charisma_lang_var*start_iat*education + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6c
summary (model6c)
anova(model6c)
```
### 3.5.3. Focus training
Training meaning secondary education/ apprenticeship 
```{r glm_outgroup_SES_focus training, echo=FALSE}

unique (Four_Out$training)
Four_Out$training = relevel(Four_Out$training , ref = "Hochschulabschluss (Master)")

lmer (penal_RTs ~ charisma_lang_var*start_iat*training + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6e
summary (model6e)
anova(model6e)
```
### 3.5.4. Sum_training
Dummy variable sum training by categorizing levels of variable training into three different categories of sum_traing, i.e. high, middle, low -> see data cleaning file
*general impact*
```{r glm_outgroup_SES_sum_train_max, echo=FALSE}

Four_Out$sum_training = relevel(Four_Out$sum_training , ref = "high")

lmer (penal_RTs ~ charisma_lang_var*start_iat*sum_training + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6a
summary (model6a)
anova(model6a)

Four_Out$sum_training = relevel(Four_Out$sum_training , ref = "middle")

lmer (penal_RTs ~ charisma_lang_var*sum_training + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6a
summary (model6a)
anova(model6a)
```
#### sum_training & gender
```{r glm_SES_train_gender, echo=FALSE}
lmer (penal_RTs ~ charisma_lang_var*sum_training*speaker_gender + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6b
summary (model6b)
anova(model6b)

lmer (penal_RTs ~ charisma_lang_var*sum_training*pp_gender + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6b
summary (model6b)
anova(model6b)
```
### 3.5.5. Sum_education
*general*
```{r glm_outgroup_SES_dum_edu, echo=FALSE}

Four_Out$sum_education = relevel(Four_Out$sum_education, ref = "high")

lmer (penal_RTs ~ charisma_lang_var*start_iat*sum_education + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model7
summary (model7)
anova(model7)
```
### 3.5.6. Subset analyses SES with sum_variables

#### Sum education
##### Subset: High education
difference 2nd blocks: lang. variety "vernacular" start iat "standard-with Charisma" vs. lang. variety "standard" start iat "vernacular-with Charisma" significantly different
```{r subset_SES_high_edu, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_high_edu,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_high_edu
summary(model1_high_edu)
anova(model1_high_edu)
emmeans(model1_high_edu, specs = pairwise ~ charisma_lang_var:start_iat)

plot_model(model1_high_edu, title = "Predicted Values of RT - high_edu", type = "int") +
  ylab ("RT")+
    xlab("mapped with Charisma")->plot_model_high_edu

#ggsave(here("Output", "Subset_high_edu_lang.varXstart.jpg"))
plot_model_high_edu
```
##### Subset: middle education
convergence issues
no impact of language variety, i.e. no difference in 2nd block
```{r subset_SES_middle_edu, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_middle_edu,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_middle_edu
summary(model1_middle_edu)
anova(model1_middle_edu)
emmeans(model1_middle_edu, specs = pairwise ~ charisma_lang_var:start_iat)
```
##### Subset: low education
```{r subset_SES_low_edu, echo=FALSE}
lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_low_edu,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_low_edu
summary(model1_low_edu)
anova(model1_low_edu)
emmeans(model1_low_edu, specs = pairwise ~ charisma_lang_var:start_iat)
```
##### Subset middle & low education
2nd block non-sig. difference
```{r subset_SES_middle_low_edu, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_middle_low_edu,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_Middle_low_edu
summary(model1_Middle_low_edu)
anova(model1_Middle_low_edu)
emmeans(model1_Middle_low_edu, specs = pairwise ~ charisma_lang_var:start_iat)

plot_model(model1_Middle_low_edu, title = "Predicted Values of RT - middle_low_edu", type = "int") +
  ylab ("RT")+
    xlab("mapped with Charisma")->plot_model_Middle_low_edu

#ggsave(here("Output", "Subset_middle_low_edu_lang.varXstart.jpg"))
plot_model_Middle_low_edu

```
#### Focus sum training
##### Subset: high training
no difference of 2nd blocks for no subsets
```{r subset_SES_sum training, echo=FALSE}
lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_high_train,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_high_train
summary(model1_high_train)
anova(model1_high_train)
emmeans(model1_high_train, specs = pairwise ~ charisma_lang_var:start_iat)
```
##### Subset: middle training
```{r subset_SES_middle_training, echo=FALSE}
lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_middle_train,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_middle_train

summary(model1_middle_train)
anova(model1_middle_train) 

emmeans(model1_middle_train, specs = pairwise ~ charisma_lang_var:start_iat)
```
##### Subset: low training summary variable
```{r subset_SES_low_training, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_low_train,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_low_train
summary(model1_low_train)
anova(model1_low_train)
emmeans(model1_low_train, specs = pairwise ~ charisma_lang_var:start_iat)
```
##### Subset: middle & low training
```{r subset_SES_sum Middle_low_train, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_middle_low_train,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_Middle_low_train
summary(model1_Middle_low_train)
anova(model1_Middle_low_train)
emmeans(model1_Middle_low_train, specs = pairwise ~ charisma_lang_var:start_iat)
```
## 3.6. SES & Populism
### all data
Impact of language variety in high education subset might be due to correlation of education with populism.
-> sum_education/ sum_training positive slopes: the lower educated the higher populism scores, biggest difference between high and middle educated
-> income less clear pattern
```{r SES_pop, echo=FALSE}
levels(Four_Out$employment_status)
levels(Four_Out$monthly_income) 

Four_Out$employment_status = relevel(Four_Out$employment_status, ref = "Vollzeit berufstätig (mehr als 30 Stunden/Woche)")

Four_Out$monthly_income = relevel(Four_Out$monthly_income, ref = "unter 500 Euro")

lm (populism_all ~ sum_education + sum_training + employment_status + monthly_income, data = Four_Out) -> model_pop_SES

summary (model_pop_SES)
anova(model_pop_SES)


ggpredict(model_pop_SES, terms = "sum_education", type = "fe")->predicted_pop_edu
ggpredict(model_pop_SES, terms = "sum_training", type = "fe")->predicted_pop_training
ggpredict(model_pop_SES, terms = "monthly_income", type = "fe")->predicted_pop_income

# plot education
predicted_pop_edu%>%ggplot(aes(x, predicted)) +
  geom_point() +
  geom_errorbar(ymin = predicted_pop_edu$conf.low, ymax = predicted_pop_edu$conf.high,
                size = 0.4, width = 0.2)+
  xlab("education")+
  ylab("populism score")->plot_pop_edu


# plot training
predicted_pop_training%>%ggplot(aes(x, predicted)) +
  geom_point() +
  geom_errorbar(ymin = predicted_pop_training$conf.low, ymax = predicted_pop_training$conf.high,
                size = 0.4, width = 0.2)+
  xlab("training")+
  ylab("populism score")->plot_pop_training

# plot income

predicted_pop_income%>%ggplot(aes(x, predicted), dodge =0.9) +
  geom_point() +
  geom_errorbar(ymin = predicted_pop_income$conf.low, ymax = predicted_pop_income$conf.high,
                size = 0.4, width = 0.2)+
  xlab("monthly income")+
  ylab("populism score")+
  theme(axis.text.x = element_text(angle = 25, hjust = 1))->plot_pop_income



plot_pop_edu
plot_pop_training
plot_pop_income
```
## 3.7. MC Social Desirebility SCale
Interaction charisma_lang_var standard:start_iat standard-with Charisma:score_MCSD sig. and negative => the stronger the socially desirable behaviour the stronger the association of standard & charisma (standard language ideology?)
```{r outgroup_MCSDs, echo=FALSE}

as.numeric(scale(Four_Out$score_MCSD))->Four_Out$score_MCSD
Four_In$start_iat = relevel(Four_In$start_iat , ref = "standard-with Charisma")
Four_In$charisma_lang_var = relevel(Four_In$charisma_lang_var , ref = "standard")



lmer (penal_RTs ~ charisma_lang_var:start_iat:score_MCSD + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model3_MCSD
summary(model3_MCSD)
anova(model3_MCSD) #score_MCSD sign
emtrends(model3_MCSD, ~ charisma_lang_var | start_iat, var = "score_MCSD")


plot_model(model3_MCSD, title = "Predicted Values of RT - MC Social Desirablility", type = "pred", terms =c("score_MCSD", "charisma_lang_var", "start_iat")) +
  ylab ("RT")+
    xlab("SD Score")->plot_model_MCSD

plot_model_MCSD
#ggsave(here("Output", "MCSD_lang.varXstart.jpg"))
```
# 4. Ingroup
convergence issues, 2nd block diff. Hochdeutsch Dialect-w/oCharisma) - (Dialekt Hochdeutsch-w/oCharisma not sign, 1st block neither
```{r glm_age_co RT_ingr ZCorr_Four_In, echo=FALSE}


#as.numeric(scale(Four_In$penal_RTs)) -> Four_In$penal_RTs
#as.numeric(scale(Four_In$age)) -> Four_In$age


Four_In$start_iat = relevel(Four_In$start_iat , ref = "standard-with Charisma")
Four_In$charisma_lang_var = relevel(Four_In$charisma_lang_var , ref = "standard")

#lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + speaker_gender + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_In,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1_in
#summary (model1_in)
#anova(model1_in)


#lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age  + (start_iat|bilendi_id) +  (charisma_lang_var|stimulus_ID), data = Four_In,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_best_in
#summary (model_best_in) # no convergence

#lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age  + (start_iat|bilendi_id) +  (1|stimulus_ID), data = Four_In,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_best_in
#summary (model_best_in)# no convergence

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age  + (1|bilendi_id) +  (1|stimulus_ID), data = Four_In,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_in_gr
summary (model_in_gr)
emmeans(model_in_gr, specs = pairwise ~ charisma_lang_var:start_iat) 

plot_model(model_in_gr, title = "Predicted Values of RT", type = "int") +
  ylab ("RT")+
    xlab("mapping with Charisma")->plot_in_group_lang.varXstart
plot_in_group_lang.varXstart
```
