---
title: "IAT_analyses - Focus political background measures"
author: "Judit Vari"
date: "21 2 2024"
output: html_document
---
This is an extract of "All_data_analyses_IAT_Audio_Swabian" focusing only on the political background measures. Generated plots are not saved in output. 
```{r libraries, include=FALSE}
library (dplyr)
library(broom)
library(ordinal)
library(lmerTest)
library(emmeans)
library(tidyverse)
library(sjPlot)
library(corrr)
library(ggcorrplot)
library(car)
library(report)
library (afex)
library(lme4)
library(optimx)
library(sjPlot)
library(ggeffects)
library(readr)
library(factoextra)
library(FactoMineR)
options(scipen=0)
```
# read cleaned data
this is cleaned data including IAT data without pre-selection phase. Cleaning included.:
- Excluded multiple participation
- excluded speeders and laggers regarding RTs (Greenwald et al.)
- excluded participants with more than 10% trials with response_time > 10000) - excluded individual trials longer than 10,000 ms
- Excluded practice blocks 1,2,5 
- Treatment of error trial response time: replaced RTs for error trials with participants' mean of correct responses plus 600 ms as penalty.

For previous steps and further analyses see Markdown files: Data_clean_Audio_Swabian_Final & Data_Analyses_IAT_Audio_Swabian
for explanation of variables see "Logger Notes Final.docx" on server
```{r read, echo=TRUE}
FourExpBlock <- read_delim(here("data_processed","IAT_clean.csv"), col_names = TRUE, delim = ",")
```
# assign classes for data
```{r assign classes, include=FALSE}

FourExpBlock$ideology <- as.numeric(FourExpBlock$ideology)
FourExpBlock$populism1 <- as.numeric(FourExpBlock$populism1)
FourExpBlock$populism2 <- as.numeric(FourExpBlock$populism2)
FourExpBlock$populism3 <- as.numeric(FourExpBlock$populism3)
FourExpBlock$populism4 <- as.numeric(FourExpBlock$populism4)
FourExpBlock$age <- as.numeric(FourExpBlock$age)
FourExpBlock$bilendi_id <- as.numeric(FourExpBlock$bilendi_id)
FourExpBlock$trialcount <- as.numeric(FourExpBlock$trialcount)
as.numeric(FourExpBlock$penal_RTs)->FourExpBlock$penal_RTs


FourExpBlock$charisma_lang_var<- as.factor(FourExpBlock$charisma_lang_var)
FourExpBlock$bundesland <- as.factor(FourExpBlock$bundesland)
FourExpBlock$education<- as.factor(FourExpBlock$education)
FourExpBlock$education_other<- as.factor(FourExpBlock$education_other)
FourExpBlock$employment_status<- as.factor(FourExpBlock$employment_status)
FourExpBlock$family_member1<- as.factor(FourExpBlock$family_member1)
FourExpBlock$family_member2<- as.factor(FourExpBlock$family_member2)
FourExpBlock$family_member3_<- as.factor(FourExpBlock$family_member3)
FourExpBlock$family_member1_other<- as.factor(FourExpBlock$family_member1_other)
FourExpBlock$family_member2_other<- as.factor(FourExpBlock$family_member2_other)
FourExpBlock$family_member3_other<- as.factor(FourExpBlock$family_member3_other)
FourExpBlock$pp_gender<- as.factor(FourExpBlock$pp_gender)
FourExpBlock$ideology_no_answer<- as.factor(FourExpBlock$ideology_no_answer)
FourExpBlock$ideology_unknown<- as.factor(FourExpBlock$ideology_unknown)
FourExpBlock$leadership_lang_var<- as.factor(FourExpBlock$leadership_lang_var)
FourExpBlock$monthly_income<- as.factor(FourExpBlock$monthly_income)
FourExpBlock$speaker_gender<- as.factor(FourExpBlock$speaker_gender)
FourExpBlock$statement1 <- as.factor(FourExpBlock$statement1)
FourExpBlock$statement2 <- as.factor(FourExpBlock$statement2)
FourExpBlock$statement3 <- as.factor(FourExpBlock$statement3)
FourExpBlock$statement4 <- as.factor(FourExpBlock$statement4)
FourExpBlock$statement5 <- as.factor(FourExpBlock$statement5)
FourExpBlock$statement6 <- as.factor(FourExpBlock$statement6)
FourExpBlock$statement7 <- as.factor(FourExpBlock$statement7)
FourExpBlock$statement8 <- as.factor(FourExpBlock$statement8)
FourExpBlock$statement9 <- as.factor(FourExpBlock$statement9)
FourExpBlock$stim_cat<- as.factor(FourExpBlock$stim_cat)
FourExpBlock$training<- as.factor(FourExpBlock$training)
FourExpBlock$training2<- as.factor(FourExpBlock$training2)
FourExpBlock$training_other<- as.factor(FourExpBlock$training_other)
FourExpBlock$training_other2<- as.factor(FourExpBlock$training_other2)
FourExpBlock$voting_behaviour<- as.factor(FourExpBlock$voting_behaviour)
FourExpBlock$voting_other<- as.factor(FourExpBlock$voting_other)
FourExpBlock$start_iat<- as.factor(FourExpBlock$start_iat)
FourExpBlock$sum_training<- as.factor(FourExpBlock$sum_training)
FourExpBlock$sum_education<- as.factor(FourExpBlock$sum_education)
FourExpBlock$family_member1_cat.response<- as.factor(FourExpBlock$family_member1_cat.response)
FourExpBlock$family_member2_cat.response<- as.factor(FourExpBlock$family_member2_cat.response)
```
# Prep IAT data:

*plots of DVs: response time (RTs) & penalised response time (error trials) & age related RTs*

```{r plots of Rt DVs, eval=FALSE, include=FALSE}

# plot normal RTs
ggplot(filtered_FourExpBlock, aes(x=response_time)) +
   ggtitle("Plot of raw Response Times") +
           geom_density()-> plot_RT



# Plot RTs penalised

ggplot(filtered_FourExpBlock, aes(x=penal_RTs)) +
  ggtitle ("Plot of Penalised Reaction Times")+
  xlab("penalised RTs")+
         geom_density()-> plot_RT_penalised



# Plot age standardised RTs


ggplot(filtered_FourExpBlock, aes(x = z_scored_RTS1))+
  ggtitle("Plot of Age standardised Reaction times")+
  xlab("z_scored_RTs")+
  geom_density()->plot_filtered_FourExpBlock

plot_RT_penalised
plot_RT
plot_filtered_FourExpBlock

```
# Prep IAT data:
## separate in- and outgropup
Separate ingroup from outgroup based on exposure to Swabian, outgroup consists of other non-standard, vernacular speakers, standard speakers and bilinguals, see data cleaning file

```{r in_out_gr, include=FALSE}
filtered_FourExpBlock%>%
  filter(family_member1_cat.response == "non_st.ingroup" | family_member2_cat.response ==  "non_st.ingroup")-> Four_In

filtered_FourExpBlock%>%
  filter(family_member1_cat.response != "non_st.ingroup" & family_member2_cat.response != "non_st.ingroup" )-> Four_Out

```
# Prep IAT data:

## separate in- and outgropup
### plots
```{r in_out_gr_plots, include=FALSE}

ggplot(Four_Out, aes(x = penal_RTs))+
  ggtitle("Penalised Reaction Times in Outgroup")+
  geom_density()+ 
  xlab("Penalised Reaction Times")->plot_Four_Out_penal_RTs
plot_Four_Out_penal_RTs

ggplot(Four_In, aes(x = penal_RTs))+
  ggtitle("Penalised Reaction Times in Ingroup")+
    geom_density()+
  xlab("Penalised Reaction Times")->plot_Four_In_penal_RTs
plot_Four_Out_penal_RTs
plot_Four_In_penal_RTs
```
# Prep IAT data:
## descriptives of data sets
```{r descriptives, echo=FALSE}
n_distinct(filtered_FourExpBlock$bilendi_id)
n_distinct(Four_Out$bilendi_id)
n_distinct(Four_In$bilendi_id)

filtered_FourExpBlock %>%
drop_na(age)%>%
  summarise(mean(age), sd (age), min (age), max (age)) -> data_pp_age_result
data_pp_age_result

Four_Out %>%
drop_na(age)%>%
  summarise(mean(age), sd (age), min (age), max (age)) -> data_pp_age_Out

Four_Out %>%
  group_by(family_member1_cat.response) %>%
  summarise(count = n_distinct(bilendi_id)) %>%
  arrange(count) -> data_pp_fam.bio1_out

data_pp_fam.bio1_out


Four_Out%>%group_by(family_member2_cat.response)%>%
  summarise(count = n_distinct(bilendi_id))%>% arrange(count)->data_pp_fam.bio2_out

bind_cols(data_pp_fam.bio1_out, data_pp_fam.bio2_out)-> data_pp_fam.bio_out
  

data_pp_age_Out
#write.table(data_pp_age_Out, "data_pp_age_Out.csv")

Four_In %>%
drop_na(age)%>%
  summarise(mean(age), sd (age), min (age), max (age)) -> data_pp_age_In
data_pp_age_In

filtered_FourExpBlock %>%
  group_by(pp_gender)%>%
  summarise(n_distinct(bilendi_id))-> data_pp_gender
data_pp_gender

Four_Out %>%
  group_by(pp_gender)%>%
  summarise(n_distinct(bilendi_id))-> data_pp_gender_Out
data_pp_gender_Out

Four_In %>%
  group_by(pp_gender)%>%
  summarise(n_distinct(bilendi_id))-> data_pp_gender_In
data_pp_gender_In

filtered_FourExpBlock %>%
   group_by(sum_training)%>%
   summarise(n_distinct(bilendi_id)) -> data_pp_training
data_pp_training

Four_Out %>%
   group_by(sum_training)%>%
   summarise(n_distinct(bilendi_id)) -> data_pp_training_Out
data_pp_training_Out

Four_Out %>%
   group_by(sum_education)%>%
   summarise(n_distinct(bilendi_id)) -> data_pp_education_Out
data_pp_education_Out
```
# correlation matrix of data sets
```{r correlations, echo=FALSE}
as.numeric(Four_Out$age)->Four_Out$age
as.numeric(Four_Out$ideology)->Four_Out$ideology
as.numeric(Four_Out$populism1)->Four_Out$populism1
as.numeric(Four_Out$populism2)->Four_Out$populism2
as.numeric(Four_Out$populism3)->Four_Out$populism3
as.numeric(Four_Out$populism4)->Four_Out$populism4

drop_na(Four_Out, age)->Four_Out
drop_na(Four_Out, ideology)->Four_Out
drop_na(Four_Out, populism1)->Four_Out
drop_na(Four_Out, populism2)->Four_Out
drop_na(Four_Out, populism3)->Four_Out
drop_na(Four_Out, populism4)->Four_Out


Four_Out%>%
  ungroup()%>%
  select(penal_RTs, age, ideology, populism1, populism2, populism3, populism4)-> bckgr_poli

cor(bckgr_poli)->matrix_bckgr_poli

matrix_bckgr_poli
# Visualize correlations


ggcorrplot(matrix_bckgr_poli, 
           title = "Background variables", hc.order = TRUE, 
           type = "lower",lab = TRUE, lab_size = 2.5,  insig = "blank")->plot_corr_matrix
plot_corr_matrix

```
# GLMS Outgroup
## general
```{r glm_outgroup__age_co, echo=FALSE}

# Max. Model regarding experimental variables


Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")
Four_Out$charisma_lang_var = relevel(Four_Out$charisma_lang_var, ref = "standard")

#lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + stim_cat + age +(charisma_lang_var:start_iat|bilendi_id) +  (charisma_lang_var|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence -> simplify RE - structure

#lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + stim_cat + age +(charisma_lang_var|bilendi_id) +  (charisma_lang_var:start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a # no convergence  -> simplify RE - structure

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + stim_cat + age +(charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a
summary (model1a)
anova(model1a)

emmeans(model1a, specs = pairwise ~ charisma_lang_var:start_iat) # 2nd block (standard vernacular-with Charisma - vernacular standard-with Charisma) sign different

plot_model(model1a, title = "Predicted values of reaction times", type = "pred", terms = c("charisma_lang_var", "start_iat")) +
  ylab ("reaction times")+
    xlab("lang. variety mapped with charisma")+
  labs(colour= str_wrap("Mapping of IAT start", width = 15))->plot_model1a
plot_model1a


#### change reference level

Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "vernacular-with Charisma")
Four_Out$charisma_lang_var = relevel(Four_Out$charisma_lang_var, ref = "vernacular")

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var  + stim_cat + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1b
summary(model1b)

```

# Outgroup 
## descriptives of political background measures 
*voting behaviour & ideology & populism*
```{r poplitical bckgr descriptives1, echo=FALSE}

# summary voting behaviour
Four_Out%>%
  group_by(voting_behaviour)%>%
  summarise(participants = n_distinct(bilendi_id))-> Four_Out_vot.behaviour

Four_Out_vot.behaviour%>%
  ggplot() +
  ggtitle("Plot of Voting Behaviour") +
  geom_col(aes(x = voting_behaviour, y = participants))+
  xlab("party")+
  ylab ("count of participants")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))->sum_voting_behaviour
sum_voting_behaviour


# summary ideology

Four_Out%>%
  ungroup()%>%
  select (bilendi_id, voting_behaviour, ideology)%>%
  distinct(bilendi_id, voting_behaviour, ideology)->Four_Out_ideology

Four_Out_ideology%>%
summarise(mean(ideology), sd(ideology), min(ideology), max (ideology))-> Four_Out_sum_ideology

Four_Out_ideology%>%
ggplot(aes(x=ideology))+
  ggtitle("Plot of political ideology") +
         geom_bar()-> Plot_sum_ideology

Plot_sum_ideology



# summary populism 

Four_Out%>%
  drop_na (populism1)%>%
  drop_na (populism2)%>%
drop_na (populism3)%>%
drop_na (populism4)->Four_Out

Four_Out%>%
  ungroup()%>%
  summarise(mean(populism1), sd(populism1), min(populism1), max (populism1), mean(populism2), sd(populism2), min(populism2), max (populism2),  mean(populism3), sd(populism3), min(populism3), max (populism3),mean(populism4), sd(populism4), min(populism4), max (populism4))-> Four_Out_sum_populism

```
# Outgroup
## Populism & PCA
*PCA shows difference of populism 4 item in comparison to items populism 1, 2, 3*
Item populism 4 from elite dimension of Akkerman et al. 2014, populism 1-3 from populism dimension
```{r PCA_outgroup_populism1, echo=FALSE}
Four_Out%>%
  ungroup()%>%
  select(bilendi_id, populism1, populism2, populism3, populism4)-> PCA_pop_data


distinct (PCA_pop_data)-> PCA_pop_data 
pca_pop <- PCA(PCA_pop_data [, 2:5], scale.unit =TRUE, graph = TRUE) # option to include quali & quanti variables


fviz_eig(pca_pop) # scree plot variance explained dimensions, keep 2

pca_pop$var$coord

pca_pop <- PCA(PCA_pop_data [, 2:5], scale.unit =TRUE,
               graph = T, ncp = 2)

summary(pca_pop)

dimdesc(pca_pop, axes = c(1,2))



p_1a <- fviz_pca_var(pca_pop,geom = c("point","text"),
                  label = "var",
                  repel = TRUE,
                  col.var = "contrib",   # colour active variables according to their contribution to PCA axes
                  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
                  title= "PCA populism"
)

p_1a 


```
# Outgroup 
## Populism & PCA

*new dimension reduction variable for populism after PCA*

```{r PCA_outgroup_populism2, echo=FALSE}


populism_dim <- pca_pop$ind$coord [,1] 

as_tibble(populism_dim)->populism_dim

bind_cols(PCA_pop_data, populism_dim)->PCA_pop_data_final

left_join (Four_Out, PCA_pop_data_final, by = c("bilendi_id", "populism1", "populism2", "populism3", "populism4"))-> Four_Out # 69164 rows (Four_Out)
  
rename (Four_Out, populism_dim = value)-> Four_Out
```
# Outgroup
## prep populism
create 2 dummy variables for populism a) mean of populism scores items 1-3, but exclude pop 4 -> PCA shows very different b) use principal component 1 as dummy

```{r poplitical bckgr prep, echo=FALSE}
Four_Out %>%
  mutate(populism_all = rowMeans(across(c(populism1, populism2, populism3), as.numeric, .names = "mean_{col}"), na.rm = TRUE)) -> Four_Out


Four_Out%>%
  distinct(bilendi_id, populism_all)%>%
ggplot(aes(x=populism_all))+
  ggtitle("Plot of Populism Mean Scores") +
         geom_bar()+
  ylab("no. of participants")+
  xlab("total score of populism items 1-3")-> Plot_sum_pop1
Plot_sum_pop1


# add new populism dimension 1 of PCA
as.numeric(Four_Out$populism_dim)-> Four_Out$populism_dim

populism_dim%>%
   ggplot(aes(x=value))+
     ggtitle("Plot of Populism Dimension") +
     geom_histogram()+
  xlab ("Populism Prinincipal Component Scores")-> Plot_sum_pop2
Plot_sum_pop2
```
# Outgroup
## prep all political background measures 
scale political bckgr variables
```{r poplitical bckgr prep2, echo=FALSE}
as.numeric(scale(Four_Out$ideology))-> Four_Out$ideology
as.numeric(scale(Four_Out$populism1))-> Four_Out$populism1
as.numeric(scale(Four_Out$populism2))-> Four_Out$populism2
as.numeric(scale (Four_Out$populism3))-> Four_Out$populism3
as.numeric(scale (Four_Out$populism4))-> Four_Out$populism4
```
# Outgroup
## prep populism
* create populism subsets*
```{r poplitical bckgr prep3, echo=FALSE}
Four_Out%>%
  ungroup()%>%
  summarise (sum(is.na(populism_all)))-> NA_no

anyNA(Four_Out$populism_all)


quantile(Four_Out$populism_all, na.rm = F) # 0% = 1;    25% = 2.666667     50%  = 3.333333     75% = 3.666667     100% = 5.0

Four_Out%>%
  filter(populism_all <= 3.333333)->Four_Out_low_pop

Four_Out%>%
  filter(populism_all >= 3.333333)->Four_Out_high_pop

n_distinct (Four_Out_high_pop$bilendi_id)
n_distinct (Four_Out_low_pop$bilendi_id)
```
## political background measures
### GLMs: Max model
```{r poplitical bckgr max model, echo=FALSE}
# Max. Model all political background measures

Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + stim_cat + age+ leadership_lang_var + populism_dim:charisma_lang_var + ideology:charisma_lang_var + voting_behaviour:charisma_lang_var  + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5
summary (model5)
anova(model5)
```
## political background measures
### focus: populism
*no impact of neither populism measure, populism_all or populism_dim
```{r poplitical bckgr pop, echo=FALSE}
# using variable populism_all (mean of 3 pop. measures)

Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")
Four_Out$charisma_lang_var = relevel(Four_Out$charisma_lang_var, ref = "standard")

#lmer (penal_RTs ~ charisma_lang_var*start_iat*populism_all + trialcount + age+ leadership_lang_var 
       # + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
#summary (model5a)
#anova(model5a) # 3 way interact. non-sign. -> drop

lmer (penal_RTs ~ charisma_lang_var*populism_all + start_iat + trialcount + age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
summary (model5a)
anova(model5a) 

# using variable populism_dim (dimension 1 of Populism PCA)

#lmer (penal_RTs ~ charisma_lang_var*start_iat*populism_dim + trialcount + age+ leadership_lang_var 
       # + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
#summary (model5a) 
#anova(model5a)  # 3 way interact. non-sign.

lmer (penal_RTs ~ charisma_lang_var*populism_dim + trialcount + start_iat+ age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
summary (model5a)
anova(model5a)

```
## political background measures
### populism
*subset analysis*
difference between 2nd blocks (charisma_lang_var*start_iat), i.e.impact of vernacular when starting with standard-with Charisma vs. impact of standard variety when starting with vernacular-with Charisma) is significant in low populism subset but not significant in high populism subset
```{r pop_subset analyses, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*start_iat+ trialcount + age+ leadership_lang_var 
       + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_high_pop, REML = T, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_pop_high
summary (model_pop_high)
anova(model_pop_high)
emmeans(model_pop_high, specs = pairwise ~ charisma_lang_var:start_iat)

lmer (penal_RTs ~ charisma_lang_var*start_iat+ trialcount + age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_low_pop,  REML = T, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_pop_low
summary (model_pop_low)
anova(model_pop_low)
emmeans(model_pop_low, specs = pairwise ~ charisma_lang_var:start_iat) 

plot_model(model_pop_high, type = "int") +
  ylab ("RT")+
    xlab("lang. variety mapped with charisma")+
  labs ( title = "Predicted values of RT", subtitle = "high populism group")+
  labs(colour="started IAT with mapping")->plot_model_pop_high
plot_model_pop_high




plot_model(model_pop_low, type = "int") +
   ylab ("RT")+
    xlab("lang. variety mapped with Charisma")+
  labs ( title = "Predicted values of RT", subtitle = "low populism group")+labs(colour="started IAT with mapping")->plot_model_pop_low
plot_model_pop_low

plot_model_pop_low

plot_model_pop_high
```
# political background measures
## populism & gender
*all outgroup data*
no impact of stimuli speaker/participant gender in complete data set with neither populism measure
```{r populism_gender, echo=FALSE}


lmer (penal_RTs ~ charisma_lang_var*populism_all*speaker_gender + start_iat + trialcount + age+ # pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5b_gender
summary (model5b_gender)
anova(model5b_gender)

lmer (penal_RTs ~ charisma_lang_var*populism_dim *speaker_gender + start_iat + trialcount + age+ # pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5d_gender
summary (model5d_gender)
anova(model5d_gender)

```
# political background measures
## populism &  gender
*subset analysis*
no impact of stimuli speaker/participant gender in different populism subsets (low and high populism) with neither populism measure
```{r pop_subset analyses gender, echo=FALSE}


lmer (penal_RTs ~ charisma_lang_var*populism_all*speaker_gender + start_iat + trialcount + age+ pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_low_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5lowPop
summary (model5lowPop)
anova(model5lowPop)

lmer (penal_RTs ~ charisma_lang_var*populism_all*speaker_gender + start_iat + trialcount + age+ pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out_high_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5highPop
summary (model5highPop)
anova(model5highPop)

```
## political background measures
### political ideology
```{r political ideology, echo=FALSE}

#as.numeric(scale(Four_Out$ideology))->Four_Out$ideology

lmer (penal_RTs ~ charisma_lang_var*start_iat*ideology + trialcount  + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5c
summary (model5c)
anova(model5c)
emtrends(model5c, ~ charisma_lang_var | start_iat, var = "ideology")

plot_model(model5c, type = "pred", terms = c("ideology", "charisma_lang_var",  "start_iat")) +
   ylab ("RT")+
    xlab ("political ideoloy left - right")+
  labs(colour="lang. variety mapped with Charisma")+
  labs ( title = "Predicted values of RT", subtitle = "grouped by started IAT with mapping")->plot_ideol_lang.varXstart
  
plot_ideol_lang.varXstart



```
## political background measures
### political ideology & gender
```{r political bckgr ideology gender, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*ideology*speaker_gender + start_iat + trialcount + age+ pp_gender + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5d
summary (model5d)
anova(model5d)
```
# political background measures
## voting behaviour
Simple effects in contrasts lang. variety level vernacular and Grün vs. LINKE, CDU/CSU vs. LINKE, AfD vs.LINKe approaching significance

```{r voting_behaviour, echo=FALSE}

Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "AfD")

lmer (penal_RTs ~ charisma_lang_var*start_iat*voting_behaviour + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5AfD
summary (model5AfD)


Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "FDP")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5FDP
summary (model5FDP) 

Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "GRüNE")

lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5grün
summary (model5grün)



Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "CDU/CSU")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5CDU
summary (model5CDU)

Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "DIE LINKE")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5links
summary (model5links)
anova(model5links)
emmeans(model5links, specs = pairwise ~ charisma_lang_var:start_iat:voting_behaviour)

plot_model(model5links, title = "Predicted Values of RT - Die LINKE", type = "pred", terms = c("charisma_lang_var", "start_iat")) +
  ylab ("RT")+
xlab("Lang. variety mapped with charisma")+
  labs(colour="started IAT with mapping") ->plot_LINKE_lang.varXstart
plot_LINKE_lang.varXstart


plot_model(model5links, type = "pred", terms = c("charisma_lang_var", "start_iat", "voting_behaviour")) +
  ggtitle("Predicted Values of RT - ref. die LINKE", subtitle = "Grouped by voting behaviour")+
  ylab ("RT")+
xlab("Lang. variety mapped with charisma")+
  labs(colour="started IAT with mapping") ->plot_pol.behaviour_lang.varXstart
plot_LINKE_lang.varXstart



Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "SPD")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5SPD
summary (model5SPD)


Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "Nichtwähler")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour*start_iat + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (start_iat|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5nonVot
summary (model5nonVot)

# voting_other

Four_Out%>%
  group_by(voting_other)%>%
summarise(n_distinct(bilendi_id))-> overview_voting_other # Frei Wähler top, but overall only 6 pp
```