---
title: "IAT_analyses"
author: "Judit Vari"
date: "21 2 2024"
output: html_document
---

```{r libraries, include=FALSE}
library (dplyr)
library(broom)
library(ordinal)
library(lmerTest)
library(emmeans)
library(tidyverse)
library(sjPlot)
library(corrr)
library(ggcorrplot)
library(car)
library(report)
library (afex)
library(lme4)
library(optimx)
library(sjPlot)
library(ggeffects)
library(readr)
library(factoextra)
library(FactoMineR)
options(scipen=0)
```
# read cleaned data
```{r read, echo=TRUE}
FourExpBlock <- read_delim("IAT_clean.csv", col_names = TRUE, delim = ",")

# this is cleaned data including IAT data without pre-selection phase. Cleaning included.:
# Excluded multiple participation
#excluded speeders and laggers regarding RTs (Greenwald et al.) excluded participants with more than 10% trials with response_time > 10000) & excluded individual trials longer than 10,000 ms
# Excluded practice blocks 1,2,5 
# Treatment of error trial response time: replaced RTs for error trials with participants' mean of correct responses plus 600 ms as penalty.

#For previous steps and further analyses see Markdown files: Data_clean_Audio_Swabian_Final & Data_Analyses_IAT_Audio_Swabian
# for explanation of variables see "Logger Notes Final.docx" on server
```
# assign classes for data
```{r assign classes, include=FALSE}

FourExpBlock$ideology <- as.numeric(FourExpBlock$ideology)
FourExpBlock$populism1 <- as.numeric(FourExpBlock$populism1)
FourExpBlock$populism2 <- as.numeric(FourExpBlock$populism2)
FourExpBlock$populism3 <- as.numeric(FourExpBlock$populism3)
FourExpBlock$populism4 <- as.numeric(FourExpBlock$populism4)
FourExpBlock$age <- as.numeric(FourExpBlock$age)
FourExpBlock$bilendi_id <- as.numeric(FourExpBlock$bilendi_id)
FourExpBlock$trialcount <- as.numeric(FourExpBlock$trialcount)
as.numeric(FourExpBlock$penal_RTs)->FourExpBlock$penal_RTs


FourExpBlock$charisma_lang_var<- as.factor(FourExpBlock$charisma_lang_var)
FourExpBlock$bundesland <- as.factor(FourExpBlock$bundesland)
FourExpBlock$education<- as.factor(FourExpBlock$education)
FourExpBlock$education_other<- as.factor(FourExpBlock$education_other)
FourExpBlock$employment_status<- as.factor(FourExpBlock$employment_status)
FourExpBlock$family_member1<- as.factor(FourExpBlock$family_member1)
FourExpBlock$family_member2<- as.factor(FourExpBlock$family_member2)
FourExpBlock$family_member3_<- as.factor(FourExpBlock$family_member3)
FourExpBlock$family_member1_other<- as.factor(FourExpBlock$family_member1_other)
FourExpBlock$family_member2_other<- as.factor(FourExpBlock$family_member2_other)
FourExpBlock$family_member3_other<- as.factor(FourExpBlock$family_member3_other)
FourExpBlock$pp_gender<- as.factor(FourExpBlock$pp_gender)
FourExpBlock$ideology_no_answer<- as.factor(FourExpBlock$ideology_no_answer)
FourExpBlock$ideology_unknown<- as.factor(FourExpBlock$ideology_unknown)
FourExpBlock$leadership_lang_var<- as.factor(FourExpBlock$leadership_lang_var)
FourExpBlock$monthly_income<- as.factor(FourExpBlock$monthly_income)
FourExpBlock$speaker_gender<- as.factor(FourExpBlock$speaker_gender)
FourExpBlock$statement1 <- as.factor(FourExpBlock$statement1)
FourExpBlock$statement2 <- as.factor(FourExpBlock$statement2)
FourExpBlock$statement3 <- as.factor(FourExpBlock$statement3)
FourExpBlock$statement4 <- as.factor(FourExpBlock$statement4)
FourExpBlock$statement5 <- as.factor(FourExpBlock$statement5)
FourExpBlock$statement6 <- as.factor(FourExpBlock$statement6)
FourExpBlock$statement7 <- as.factor(FourExpBlock$statement7)
FourExpBlock$statement8 <- as.factor(FourExpBlock$statement8)
FourExpBlock$statement9 <- as.factor(FourExpBlock$statement9)
FourExpBlock$stim_cat<- as.factor(FourExpBlock$stim_cat)
FourExpBlock$training<- as.factor(FourExpBlock$training)
FourExpBlock$training2<- as.factor(FourExpBlock$training2)
FourExpBlock$training_other<- as.factor(FourExpBlock$training_other)
FourExpBlock$training_other2<- as.factor(FourExpBlock$training_other2)
FourExpBlock$voting_behaviour<- as.factor(FourExpBlock$voting_behaviour)
FourExpBlock$voting_other<- as.factor(FourExpBlock$voting_other)
FourExpBlock$start_iat<- as.factor(FourExpBlock$start_iat)
FourExpBlock$sum_training<- as.factor(FourExpBlock$sum_training)
FourExpBlock$sum_education<- as.factor(FourExpBlock$sum_education)
FourExpBlock$family_member1_cat.response<- as.factor(FourExpBlock$family_member1_cat.response)
FourExpBlock$family_member2_cat.response<- as.factor(FourExpBlock$family_member2_cat.response)
```
# seperate in- and outgropup
```{r separate in_out, include=FALSE}
FourExpBlock%>%
  filter(family_member1_cat.response == "non_st.ingroup" | family_member2_cat.response ==  "non_st.ingroup")-> Four_In

FourExpBlock%>%
  filter(family_member1_cat.response != "non_st.ingroup" & family_member2_cat.response != "non_st.ingroup" )-> Four_Out
```

# descriptives of data sets
```{r descriptives, include=FALSE}
FourExpBlock %>%
drop_na(age)%>%
  summarise(mean(age), sd (age), min (age), max (age)) -> data_pp_age_result
data_pp_age_result

Four_Out %>%
  ungroup()%>%
drop_na(age)%>%
  summarise(mean(age), sd (age), min (age), max (age)) -> data_pp_age_Out
data_pp_age_Out
#write.table(data_pp_age_Out, "data_pp_age_Out.csv")

Four_In %>%
  ungroup()%>%
  drop_na(age)%>%
  summarise(mean(age), sd (age), min (age), max (age)) -> data_pp_age_In
data_pp_age_In

FourExpBlock %>%
  group_by(pp_gender)%>%
  summarise(n_distinct(bilendi_id))-> data_pp_gender
data_pp_gender

Four_Out %>%
  group_by(pp_gender)%>%
  summarise(n_distinct(bilendi_id))-> data_pp_gender_Out
data_pp_gender_Out

Four_In %>%
  group_by(pp_gender)%>%
  summarise(n_distinct(bilendi_id))-> data_pp_gender_In
data_pp_gender_In


FourExpBlock %>%
   group_by(sum_training)%>%
   summarise(n_distinct(bilendi_id)) -> data_pp_training
data_pp_training

Four_Out %>%
   group_by(sum_training)%>%
   summarise(n_distinct(bilendi_id)) -> data_pp_training_Out
data_pp_training_Out

Four_In %>%
   group_by(sum_training)%>%
   summarise(n_distinct(bilendi_id)) -> data_pp_training_In
data_pp_training_In

Four_Out %>%
   group_by(sum_education)%>%
   summarise(n_distinct(bilendi_id)) -> data_pp_education_Out
data_pp_education_Out

Four_In %>%
   group_by(sum_education)%>%
   summarise(n_distinct(bilendi_id)) -> data_pp_education_In
data_pp_education_In
```
# correlation matrix of data sets
```{r Prep: correlations, echo=FALSE}
Four_Out%>%
drop_na(age)%>%
drop_na(ideology)%>%
drop_na(populism1)%>%
drop_na(populism2)%>%
drop_na(populism3)%>%
drop_na(populism4)%>%
  ungroup()%>%
  select(age, score_MCSD, penal_RTs, ideology, populism1, populism2, populism3, populism4)-> bckgr_poli

cor(bckgr_poli)->matrix_bckgr_poli

matrix_bckgr_poli
# Visualize correlations


ggcorrplot(matrix_bckgr_poli, 
           title = "Background variables", hc.order = TRUE, 
           type = "lower",lab = TRUE, lab_size = 2.5,  insig = "blank")
```
# GLMS Outgroup
## general
```{r glm_outgroup__age_co, echo=FALSE}

# prep
as.numeric(scale(Four_Out$penal_RTs)) -> Four_Out$
penal_RTs
as.numeric(scale(Four_Out$age)) -> Four_Out$age

# plot response_time

ggplot(Four_Out, aes(x=penal_RTs)) +
         geom_density()-> plot_RT_Four

plot_RT_Four # 

# Max. Model

# ensure ref level
Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")
Four_Out$charisma_lang_var = relevel(Four_Out$charisma_lang_var, ref = "standard")

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + stim_cat + age +(charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1a
summary (model1a)
anova(model1a)

emmeans(model1a, specs = pairwise ~ charisma_lang_var:start_iat) # 2nd block diff. non sign impact

plot_model(model1a, title = "Predicted Values of RT", type = "pred", terms = c("charisma_lang_var", "start_iat")) +
  ylab ("RT")+
    xlab("mapped with Charisma")->plot_model1a
plot_model1a



# best fit model
drop1(model1a)

## drop "charisma_lang_var:speaker_gender" & "charisma_lang_var:pp_gender" & " charisma_lang_var:sum_training" non.sign 

Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_int_best1

summary(model1_int_best1)
anova(model1_int_best1) 

emmeans(model1_int_best1, specs = pairwise ~ charisma_lang_var:start_iat) # 2nd block diff. signf. vernacular standard-with Charisma) - (standard vernacular-with Charisma)

#### change reference level

Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "vernacular-with Charisma")

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var  + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model2_int_best1

summary(model2_int_best1)


plot_model(model2_int_best1, title = "Predicted Values of RT", type = "int") +
  ylab ("RT")+
    xlab("mapping with Charisma")->plot_int_best2
plot_int_best2

ggsave( filename = "plot_int_best.jpg", plot= plot_int_best2)
```
# Outgroup 
## Populism & PCA
```{r PCA_outgroup_populism, echo=FALSE}
# PCA populism

Four_Out%>%
  ungroup()%>%
  select(bilendi_id, populism1, populism2, populism3, populism4)-> PCA_pop_data

n_distinct(PCA_pop_data$bilendi_id) # 577 pp

distinct (PCA_pop_data)-> PCA_pop_data ##  577 pp

pca_pop <- PCA(PCA_pop_data [, 2:5], scale.unit =TRUE, graph = TRUE) # option to include quali & quanti variables


fviz_eig(pca_pop) # scree plot variance explained dimensions, keep 2

pca_pop$var$coord

pca_pop <- PCA(PCA_pop_data [, 2:5], scale.unit =TRUE,
               graph = T, ncp = 2)

summary(pca_pop)

dimdesc(pca_pop, axes = c(1,2))



p_1a <- fviz_pca_var(pca_pop,geom = c("point","text"),
                  label = "var",
                  repel = TRUE,
                  col.var = "contrib",   # colour active variables according to their contribution to PCA axes
                  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
                  title= "PCA populism"
)

p_1a # populism 4 different to populism 1, 2, 3,



# new dimension reduction variable fro populism after PCA


populism_dim <- pca_pop$ind$coord [,1] 

as_tibble(populism_dim)->populism_dim # 577

bind_cols(PCA_pop_data, populism_dim)->PCA_pop_data_final

left_join (Four_Out, PCA_pop_data_final, by = c("bilendi_id", "populism1", "populism2", "populism3", "populism4"))-> Four_Out # 69164 rows (Four_Out)
  
rename (Four_Out, populism_dim = value)-> Four_Out

```
# Outgroup
## political background measures
### prep
```{r poplitical bckgr prep, echo=FALSE}
# summary voting behaviour
as.factor(Four_Out$voting_behaviour)-> Four_Out$voting_behaviour
Four_Out%>%
  group_by(voting_behaviour)%>%
  summarise(n_distinct(bilendi_id))-> Four_Out_vot.behaviour
Four_Out_vot.behaviour

ggplot(Four_Out, aes(x = voting_behaviour)) +
  geom_bar()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))->sum_voting_behaviour
sum_voting_behaviour

# summary ideology

Four_Out%>%
  ungroup()%>%
summarise(mean(ideology), sd(ideology), min(ideology), max (ideology))-> Four_Out_sum_ideology
Four_Out_sum_ideology

ggplot(Four_Out, aes(x=ideology))+
         geom_bar()-> Plot_sum_ideology
Plot_sum_ideology


# summary populism
drop_na (Four_Out, populism1)->Four_Out
drop_na (Four_Out, populism2)->Four_Out
drop_na (Four_Out, populism3)->Four_Out
drop_na (Four_Out, populism4)->Four_Out

Four_Out%>%
  ungroup()%>%
  summarise(mean(populism1), sd(populism1), min(populism1), max (populism1), mean(populism2), sd(populism2), min(populism2), max (populism2),  mean(populism3), sd(populism3), min(populism3), max (populism3),mean(populism4), sd(populism4), min(populism4), max (populism4))-> Four_Out_sum_populism
Four_Out_sum_populism

# create 2 new populism summary variables but exclude pop 4 -> PCS show very different

# just average


Four_Out %>%
  mutate(populism_all = rowMeans(across(c(populism1, populism2, populism3), as.numeric, .names = "mean_{col}"), na.rm = TRUE)) -> Four_Out

ggplot(Four_Out, aes(x=populism_all))+
         geom_bar() -> Plot_sum_pop1
Plot_sum_pop1

# add new populism dimension 1 of PCA
as.numeric(Four_Out$populism_dim)-> Four_Out$populism_dim

ggplot(Four_Out, aes(x=populism_dim))+
         geom_histogram()-> Plot_sum_pop2
Plot_sum_pop2


# scale political bckgr variables
as.numeric(scale(Four_Out$ideology))-> Four_Out$ideology
as.numeric(scale(Four_Out$populism1))-> Four_Out$populism1
as.numeric(scale(Four_Out$populism2))-> Four_Out$populism2
as.numeric(scale (Four_Out$populism3))-> Four_Out$populism3
as.numeric(scale (Four_Out$populism4))-> Four_Out$populism4


# create populism subset


quantile(Four_Out$populism_all, na.rm = F) # 0% = 1;    25% = 2.666667     50%  = 3.333333     75% = 3.666667     100% = 5.0

Four_Out%>%
  filter(populism_all <= 3.333333)->Four_Out_low_pop

Four_Out%>%
  filter(populism_all >= 3.333333)->Four_Out_high_pop

n_distinct (Four_Out_high_pop$bilendi_id)#309
n_distinct (Four_Out_low_pop$bilendi_id) # 268
```
## political background measures
### GLMs: Max model
```{r poplitical bckgr max model, include=FALSE}
# Max. Model all political background measures

Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + stim_cat + age+ leadership_lang_var + populism_dim:charisma_lang_var + ideology:charisma_lang_var + voting_behaviour:charisma_lang_var  + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5
summary (model5)
anova(model5)
```
## political background measures
### GLMs: only populism: populism_all & populism_dim
```{r poplitical bckgr pop, echo=FALSE}

# using variable populism_all (mean of 3 pop. measures)

Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")
Four_Out$charisma_lang_var = relevel(Four_Out$charisma_lang_var, ref = "standard")

lmer (penal_RTs ~ charisma_lang_var*start_iat*populism_all + trialcount + age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
summary (model5a)
anova(model5a) # 3 way interact. non-sign. -> drop

lmer (penal_RTs ~ charisma_lang_var*populism_all + start_iat + trialcount + age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
summary (model5a)
anova(model5a) 

# using variable populism_dim (dimension 1 of Populism PCA)

lmer (penal_RTs ~ charisma_lang_var*start_iat*populism_dim + trialcount + age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
summary (model5a) 
anova(model5a)  # 3 way interact. non-sign.

lmer (penal_RTs ~ charisma_lang_var*populism_dim + trialcount + start_iat+ age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5a
summary (model5a)
anova(model5a)

# subsets populism: high and low

lmer (penal_RTs ~ charisma_lang_var*start_iat+ trialcount + age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_high_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_pop_high
summary (model_pop_high)
anova(model_pop_high)
emmeans(model_pop_high, specs = pairwise ~ charisma_lang_var:start_iat)# diff. 2nd block (vernacular standard-with Charisma & standard vernacular-with Charisma) not. sign -> z ratio: 2.015  p = 0.1822

lmer (penal_RTs ~ charisma_lang_var*start_iat+ trialcount + age+ leadership_lang_var 
        + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_low_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model_pop_low
summary (model_pop_low)
anova(model_pop_low)
emmeans(model_pop_low, specs = pairwise ~ charisma_lang_var:start_iat) # diff. 2nd block (vernacular standard-with Charisma & standard vernacular-with Charisma) sign.   z-ratio: 2.724  p= 0.0327  

plot_model(model_pop_high, title = "Predicted Values of RT - -high populism", type = "int") +
  ylab ("RT")+
    xlab("mapped with Charisma")->plot_model_pop_high

plot_model(model_pop_low, title = "Predicted Values of RT -low populism", type = "int") +
  ylab ("RT")+
    xlab("mapped with Charisma")->plot_model_pop_low


plot_model_pop_low

plot_model_pop_high

## populism & gender
### all Outgroup data

lmer (penal_RTs ~ charisma_lang_var*populism_all*speaker_gender + trialcount + age+ # pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5b
summary (model5b)
anova(model5b)

lmer (penal_RTs ~ charisma_lang_var*populism_dim *speaker_gender + trialcount + age+ # pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5b
summary (model5b)
anova(model5b)

## with subsets low & high pop

lmer (penal_RTs ~ charisma_lang_var*populism_all*speaker_gender + trialcount + age+ pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_low_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5b
summary (model5b)
anova(model5b)

lmer (penal_RTs ~ charisma_lang_var*populism_all*speaker_gender + trialcount + age+ pp_gender
        + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_high_pop,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5b
summary (model5b)
anova(model5b)



```
# political background measures
## political ideology
```{r political bckgr ideology, echo=FALSE}

lmer (penal_RTs ~ charisma_lang_var*ideology + trialcount  + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5c
summary (model5c)
anova(model5c)

## ideology & gender

lmer (penal_RTs ~ charisma_lang_var*ideology*speaker_gender + trialcount + age+ pp_gender + leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5d
summary (model5d)
anova(model5d)

```
# political background measures
## voting behaviour

```{r voting_behave, echo=FALSE}
unique(Four_Out$voting_behaviour)

Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "AfD")

lmer (penal_RTs ~ charisma_lang_var*voting_behaviour + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5e
summary (model5e) # sign. diff. AfD & andere


Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "FDP")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5e
summary (model5e) # approaching sign. diff. FDP & andere

Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "GR체NE")

lmer (penal_RTs ~ charisma_lang_var*voting_behaviour + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5e
summary (model5e)

Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "CDU/CSU")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5e
summary (model5e)

Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "DIE LINKE")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5e
summary (model5e)

Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "SPD")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5e
summary (model5e)


Four_Out$voting_behaviour = relevel(Four_Out$voting_behaviour, ref = "Nichtw채hler")
lmer (penal_RTs ~ charisma_lang_var*voting_behaviour + trialcount + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model5e
summary (model5e)

# voting_other

Four_Out%>%
  group_by(voting_other)%>%
summarise(n_distinct(bilendi_id))-> overview_voting_other # Frei W채hler top, but overall only 6 pp
```
# Outgroup
## SES
```{r glm_outgroup_SES_measures, echo=FALSE}
as.factor(Four_Out$education)-> Four_Out$education
as.factor(Four_Out$employment_status)-> Four_Out$employment_status
as.factor(Four_Out$monthly_income)-> Four_Out$monthly_income
as.factor(Four_Out$training)-> Four_Out$training
as.factor(Four_Out$training2)-> Four_Out$training2
as.factor(Four_Out$training_other)-> Four_Out$training_other
as.factor(Four_Out$training_other2)-> Four_Out$training_other2
as.factor(Four_Out$sum_training)-> Four_Out$sum_training
as.factor(Four_Out$sum_education)-> Four_Out$sum_education

Four_Out%>%
  group_by(education)%>%
summarise(n_distinct(bilendi_id))-> overview_education

Four_Out%>%
  group_by(monthly_income)%>%
summarise(n_distinct(bilendi_id))-> overview_monthly_income

# GLMs

# Max. Model

Four_Out$start_iat = relevel(Four_Out$start_iat , ref = "standard-with Charisma")

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + stim_cat + 
        #age+ 
        leadership_lang_var + sum_education:charisma_lang_var + employment_status:charisma_lang_var + sum_training:charisma_lang_var  + monthly_income:charisma_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6
summary (model6) # simple effects for charisma_lang_varvernacular:education Realschulabschluss, Mittlere Reife, Fachschulreife oder Abschluss der polytechnischen Oberschule 10. Klasse, as well as Azubi/Sch체lerIn

anova(model6)

# sum_training

unique(Four_Out$sum_training)
drop_na(Four_Out, sum_training)-> Four_Out
unique(Four_Out$sum_training)


Four_Out$sum_training = relevel(Four_Out$sum_training , ref = "high")

lmer (penal_RTs ~ charisma_lang_var*sum_training + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6a
summary (model6a)
anova(model6a)

Four_Out$sum_training = relevel(Four_Out$sum_training , ref = "middle")

lmer (penal_RTs ~ charisma_lang_var*sum_training + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6a
summary (model6a)
anova(model6a)

  ## sum_training & gender

lmer (penal_RTs ~ charisma_lang_var*sum_training*speaker_gender + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6b
summary (model6b)
anova(model6b)

lmer (penal_RTs ~ charisma_lang_var*sum_training*pp_gender + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6b
summary (model6b)
anova(model6b)

# overall: education

unique(Four_Out$education)
Four_Out$education = relevel(Four_Out$education , ref = "Abitur bzw. erweiterte Oberschule mit Abschluss 12. Klasse (Hochschulreife)")


lmer (penal_RTs ~ charisma_lang_var*education + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6c
summary (model6c) # approaching sig. simple effects for middle education: Realschulabschluss, Mittlere Reife, Fachschulreife oder Abschluss der polytechnischen Oberschule 10. Klasse
anova(model6c)

Four_Out$education = relevel(Four_Out$education , ref = "Hauptschulabschluss, Volksschulabschluss, Abschluss der polytechnischen Oberschule 8. oder 9. Klasse")
lmer (penal_RTs ~ charisma_lang_var*education + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6c
summary (model6c)




# overall: monthly_income

lmer (penal_RTs ~ charisma_lang_var*monthly_income + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6d
summary (model6d)
anova(model6d)


# overall: training

unique (Four_Out$training)
Four_Out$training = relevel(Four_Out$training , ref = "Hochschulabschluss (Master)")

lmer (penal_RTs ~ charisma_lang_var*training + trialcount + stim_cat + age+ leadership_lang_var + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model6e
summary (model6e) # approaching sign. simple effect for charisma_lang_varvernacular:trainingKeinen                                                                    -1.869
anova(model6e)
```
# Outgroup
## Subset analyses SES
```{r subset_outgroup_SES_measures, echo=FALSE}
Four_Out%>%
  filter(sum_training == "high")-> Four_Out_high_train
Four_Out%>%
  filter(sum_training == "middle")-> Four_Out_middle_train
Four_Out%>%
  filter(sum_training == "low")-> Four_Out_low_train
Four_Out%>%
  filter(sum_training == "middle" | sum_training == "low")-> Four_Out_middle_low_train


Four_Out%>%
  filter(sum_education == "high")-> Four_Out_high_edu
Four_Out%>%
  filter(sum_education == "middle")-> Four_Out_middle_edu
Four_Out%>%
  filter(sum_education == "low")-> Four_Out_low_edu
Four_Out%>%
  filter(sum_education == "middle" | sum_education == "low")-> Four_Out_middle_low_edu

# High training

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_high_train,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_high_train
summary(model1_high_train)
anova(model1_high_train)
emmeans(model1_high_train, specs = pairwise ~ charisma_lang_var:start_iat)

# high education

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_high_edu,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_high_edu
summary(model1_high_edu)
anova(model1_high_edu)
emmeans(model1_high_edu, specs = pairwise ~ charisma_lang_var:start_iat) # vernacular standard-with Charisma) - (standard vernacular-with Charisma) 2nd block sign.


# Middle training

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_middle_train,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_middle_train

summary(model1_middle_train)
anova(model1_middle_train) 

emmeans(model1_middle_train, specs = pairwise ~ charisma_lang_var:start_iat)

# Middle education

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_middle_edu,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_middle_edu
summary(model1_middle_edu)
anova(model1_middle_edu)
emmeans(model1_middle_edu, specs = pairwise ~ charisma_lang_var:start_iat)


#Low training

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_low_train,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_low_train
summary(model1_low_train)
anova(model1_low_train)
emmeans(model1_low_train, specs = pairwise ~ charisma_lang_var:start_iat)

# Low education
lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_low_edu,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_low_edu
summary(model1_low_edu)
anova(model1_low_edu)
emmeans(model1_low_edu, specs = pairwise ~ charisma_lang_var:start_iat) # vernacular standard-with Charisma) - (standard vernacular-with Charisma) 2nd block sign.

# Middle & Low training
lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_middle_low_train,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_Middle_low_train
summary(model1_Middle_low_train)
anova(model1_Middle_low_train)
emmeans(model1_Middle_low_train, specs = pairwise ~ charisma_lang_var:start_iat)

# Middle & Low education
lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out_middle_low_edu,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model1_Middle_low_edu
summary(model1_Middle_low_edu)
anova(model1_Middle_low_edu)
emmeans(model1_Middle_low_edu, specs = pairwise ~ charisma_lang_var:start_iat)

plot_model(model1_Middle_low_edu, title = "Predicted Values of RT - middle_low_edu", type = "int") +
  ylab ("RT")+
    xlab("mapped with Charisma")->plot_model_Middle_low_edu

plot_model(model1_Middle_low_edu, title = "Predicted Values of RT - middle_low_edu", type = "int") +
  ylab ("RT")+
    xlab("mapped with Charisma")->plot_model_Middle_low_edu

plot_model(model1_high_edu, title = "Predicted Values of RT - high_edu", type = "int") +
  ylab ("RT")+
    xlab("mapped with Charisma")->plot_model_high_edu

plot_model_Middle_low_edu
plot_model_high_edu
# no difference of 2nd blocks, but in high edu (sig) & low edu (sig)
# sample size? difference high edu (sig) & middle_low edu (non-sig) => in line with hypothesis?
```
# Outgroup
## MC Social Desirebility SCale
```{r outgroup_MCSDs, echo=FALSE}

as.numeric(scale(Four_Out$score_MCSD))->Four_Out$score_MCSD
Four_In$start_iat = relevel(Four_In$start_iat , ref = "standard-with Charisma")
Four_In$charisma_lang_var = relevel(Four_In$charisma_lang_var , ref = "standard")



lmer (penal_RTs ~ charisma_lang_var:start_iat:score_MCSD + trialcount + age+ leadership_lang_var + stim_cat + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_Out,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))-> model3_MCSD
summary(model3_MCSD)
anova(model3_MCSD) #score_MCSD sign
emtrends(model3_MCSD, ~ charisma_lang_var | start_iat, var = "score_MCSD") # charisma_lang_varstandard:start_iatstandard-with Charisma:score_MCSD sig. and negative => the stronger the socially desirbale behaviour the stronger the association of standard & charisma (standard language ideology?)


plot_model(model3_MCSD, title = "Predicted Values of RT - MC Social Desirebility", type = "pred", terms =c("score_MCSD", "charisma_lang_var", "start_iat")) +
  ylab ("RT")+
    xlab("SD Score")->plot_model_MCSD

plot_model_MCSD

```
# Ingroup

```{r glm_age_co RT_ingr ZCorr_Four_In, echo=FALSE}


as.numeric(scale(Four_In$penal_RTs)) -> Four_In$penal_RTs
as.numeric(scale(Four_In$age)) -> Four_In$age


Four_In$start_iat = relevel(Four_In$start_iat , ref = "standard-with Charisma")

lmer (penal_RTs ~ charisma_lang_var*start_iat + trialcount + age+ leadership_lang_var + speaker_gender + (charisma_lang_var|bilendi_id) +  (1|stimulus_ID), data = Four_In,  REML = TRUE, lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) -> model1_in
summary (model1_in)
anova(model1_in)
emmeans(model1_in, specs = pairwise ~ charisma_lang_var:start_iat) # 2nd block diff. not sign